---
title: "Bonacolta_Pcla_2022"
author: "Anthony Mario Bonacolta"
date: "November 1st, 2022"
output: html_document
---

# Load Packages
```{r Packages, include=FALSE}
library(phyloseq); packageVersion("phyloseq")
library(Biostrings); packageVersion("Biostrings")
library(ggplot2); packageVersion("ggplot2")
library(ALDEx2);packageVersion("ALDEx2")
library(vegan); packageVersion("vegan")
library(viridis); packageVersion("viridis")
library(tidyr); packageVersion("tidyr")
library("plyr"); packageVersion("plyr")
library("dplyr"); packageVersion("dplyr")
library("scales"); packageVersion("scales")
library("grid"); packageVersion("grid")
library("reshape2"); packageVersion("reshape2")
library("edgeR"); packageVersion("edgeR")
library("tidyr"); packageVersion("tidyr")
library("viridis"); packageVersion("viridis")
library("gridExtra"); packageVersion("gridExtra")
library("ape"); packageVersion("ape")
library("microbiome"); packageVersion("microbiome")
library(ggjoy); packageVersion("ggjoy")
library(ggtree); packageVersion("ggtree")
library(ggstance); packageVersion("ggstance")
library(ape); packageVersion("ape")
library("tidyverse"); packageVersion("tidyverse")
library(phylotools);packageVersion("phylotools")
```

# Load Data and Filter Data
## Bacteriome
```{r, echo=TRUE}
SV_bac <- read.table("~/raw_data/16S/Bonacolta_Pcla_16S_ASVs_counts.tsv", row.names = 1, check.names= FALSE, sep = "\t", header = TRUE)
tax_bac <-as.matrix(read.table("~/raw_data/16S/Bonacolta_Pcla_16S_ASVs_taxonomy.txt", row.names = 1, header = TRUE, sep = "\t"))
map_bac <- read.table("~/raw_data/16S/Bonacolta_Pcla_16S_map.txt", row.names = 1, sep ="\t", header = TRUE)
#tree_bac <- read.tree(file = "/Volumes/projects/bonacolta/pcla/paramuricea_bacteriome/new/analysis/tree-new.nw")
dat_bac <- read_csv("~/raw_data/16S/ASV_names.csv",col_names = TRUE)
dat_bac <- data.frame(dat_bac)
#new_tree <- sub.taxa.label(tree_bac, dat_bac)
ps_bac = phyloseq(otu_table(SV_bac, taxa_are_rows=TRUE), 
               sample_data(map_bac), 
               tax_table(tax_bac))

sample_data(ps_bac)$resitance_14_21 = recode(sample_data(ps_bac)$resitance_14_21,
                                  Hypersensible = "Hyper Sensitive",
                                  Sensible = "Sensitive",
                                  Resistant = "Resistant",
                                  Superresistant = "Super Resistant")

psf_bac <- subset_taxa(ps_bac, (Order!="Chloroplast"| is.na(Order)))
psf_bac<- subset_taxa(psf_bac, (Family!="Mitochondria"| is.na(Family)))
psf_bac <- prune_samples(sample_sums(psf_bac)>=250, psf_bac)
f1<- filterfun_sample(topf(0.99))
wh1 <- genefilter_sample(psf_bac, f1, A=2)
psf_bac <- prune_taxa(wh1, psf_bac)
psf_bac_coral<- subset_samples(psf_bac, psf_bac@sam_data$rack!='food')
psf_bac_coral <- subset_samples(psf_bac_coral, psf_bac_coral@sam_data$rack!='water')
psf_bac_coral_Tmin <- subset_samples(psf_bac_coral, psf_bac_coral@sam_data$time=='T-1')
psf_bac_coral_Tmin
```
**92 samples**

## Eukaryome
```{r, echo=TRUE}
SV_euk <- read.table("~/raw_data/18S/Bonacolta_Pcla_18S_ASVs_counts.tsv", row.names = 1, check.names= FALSE, sep = "\t", header = TRUE)
tax_euk <-as.matrix(read.table("/~/raw_data/18S/Bonacolta_Pcla_18S_ASVs_taxonomy.txt", row.names = 1, header = TRUE, sep = "\t"))
map_euk <- read.table("~/raw_data/18S/Bonacolta_Pcla_18S_map.txt", row.names = 1, sep ="\t", header = TRUE)
#tree_euk <- read.tree(file = "/Volumes/projects/bonacolta/pcla/paramuricea_eukaryome/new/analysis/FastTree_pcla_18S")

ps_euk = phyloseq(otu_table(SV_euk, taxa_are_rows=TRUE), 
               sample_data(map_euk), 
               tax_table(tax_euk))

sample_data(ps_euk)$resitance_14_21 = recode(sample_data(ps_euk)$resitance_14_21,
                                  Hypersensible = "Hyper Sensitive",
                                  Sensible = "Sensitive",
                                  Resistant = "Resistant",
                                  Superresistant = "Super Resistant")

psf_euk<- subset_taxa(ps_euk, (Order!="Chloroplast"| is.na(Order)))
psf_euk <- subset_taxa(psf_euk, (Family!="Mitochondria"| is.na(Family)))
psf_euk <- subset_taxa(psf_euk, (Division!="Metazoa"| is.na(Division)))
psf_euk <- subset_taxa(psf_euk, (Class!="Embryophyceae"| is.na(Class)))
psf_euk <- prune_samples(sample_sums(psf_euk)>=250, psf_euk)
f1<- filterfun_sample(topf(0.99))
wh1 <- genefilter_sample(psf_euk, f1, A=2)
psf_euk<- prune_taxa(wh1, psf_euk)
psf_euk_coral<- subset_samples(psf_euk, psf_euk@sam_data$rack!='food')
psf_euk_coral <- subset_samples(psf_euk_coral, psf_euk_coral@sam_data$rack!='water')
psf_euk_coral_Tmin <- subset_samples(psf_euk_coral, psf_euk_coral@sam_data$time=='T-1')
psf_euk_coral_Tmin

noport <- subset_samples(psf_euk_coral_Tmin, psf_euk_coral_Tmin@sam_data$region!="Portugal")
noport_bac <- subset_samples(psf_bac_coral_Tmin, psf_bac_coral_Tmin@sam_data$region!="Portugal")
```
**138 samples**

## Other files and color palettes
```{r misc, include=FALSE}
euk_classes_csv <- read.csv("/Volumes/projects/bonacolta/pcla/paramuricea_eukaryome/new/analysis/sorted_euk_classes.txt",header=F)
euk_classes <- euk_classes_csv %>% pull(V1)
euk_families_csv <- read.csv("/Volumes/projects/bonacolta/pcla/paramuricea_eukaryome/new/analysis/sorted_euk_families.txt",header=F)
euk_families <- euk_families_csv %>% pull(V1)
euk_orders_csv <- read.csv("/Volumes/projects/bonacolta/pcla/paramuricea_eukaryome/new/analysis/sorted_euk_orders.txt",header=F)
euk_orders <- euk_orders_csv %>% pull(V1)

bac_classes_csv <- read.csv("/Volumes/projects/bonacolta/pcla/paramuricea_bacteriome/new/analysis/sorted_bac_classes.txt",header=F)
bac_classes <- bac_classes_csv %>% pull(V1)
bac_families_csv <- read.csv("/Volumes/projects/bonacolta/pcla/paramuricea_bacteriome/new/analysis/sorted_bac_families.txt",header=F)
bac_families <- bac_families_csv %>% pull(V1)
bac_orders_csv <- read.csv("/Volumes/projects/bonacolta/pcla/paramuricea_bacteriome/new/analysis/sorted_bac_orders.txt",header=F)
bac_orders <- bac_orders_csv %>% pull(V1)

library(randomcoloR)
n <- 50

palette <- distinctColorPalette(n)


c25 <- c(
  "dodgerblue2", "#E31A1C", # red
  "green4",
  "#6A3D9A", # purple
  "#FF7F00", # orange
  "black", "gold1",
  "skyblue2", "#FB9A99", # lt pink
  "palegreen2",
  "#CAB2D6", # lt purple
  "#FDBF6F", # lt orange
  "gray70", "khaki2",
  "maroon", "orchid1", "deeppink1", "blue1", "steelblue4",
  "darkturquoise", "green1", "yellow4", "yellow3",
  "darkorange4", "brown"
)

#ordered<- c("Balun", "Mana","Altare","Indiano","Lighthouse","Gargallu","Palazzinu","Palazzu","La Vaca","Pota de Llop", "Tascons","Sagres")
ordered<- c("Sagres","Tascons","Pota de Llop","La Vaca","Palazzu","Palazzinu","Gargallu","Lighthouse","Indiano","Altare","Mana","Balun")

```


# Figures
## Figure 1A. Bubble Plot of  Bac Populations (w/ Portugal)
```{r}
bub1 <- merge_samples(psf_bac_coral_Tmin, "population") 
type_taxa1 <- bub1 %>% 
  tax_glom(taxrank = "Order") %>% 
  transform_sample_counts(function(x) {x/sum(x)*100} )  

type_taxa1 <- type_taxa1 %>% 
  psmelt() %>% 
  arrange(Abundance) 

library(data.table)
# create dataframe from phyloseq object
dat1 <- data.table(type_taxa1)
# convert Phylum to a character vector from a factor because R
dat1$Order <- as.character(dat1$Order)
# group dataframe by Phylum, calculate median rel. abundance
dat1[, median := median(Abundance, na.rm = FALSE), 
    by = "Order"]
# Change name to remainder of Phylum less than 2%
dat1[(median <= 0.01), Order := "Below Threshold"]
dat1[(Order == "Below Threshold"), Phylum := "Other"]
#dat1[(median <= 0.10), Phylum := "Other"]

dat1$Order[dat1$Order == "Omnitrophia_NA"] <- "Omnitrophia IS"
dat1$Order[dat1$Order == "Gammaproteobacteria_NA"] <- "Gammaproteobacteria IS"
dat1$Order[dat1$Order == "Bacilli_NA"] <- "Bacilli IS"
dat1$Order[dat1$Order == "Bacteria_NA"] <- "Bacteria IS"
dat1$Order[dat1$Order == "Apicomplexa_X"] <- "Apicomplexa IS"
dat1$Order[dat1$Order == "Alveolata_NA"] <- "Alveolata IS"
dat1$Order[dat1$Order == "Bacillariophyta_X"] <- "Bacillariophyta IS"
dat1$Order[dat1$Order == "Syndiniales_X"] <- "Syndiniales IS"
dat1$Order[dat1$Order == "Dinoflagellata_NA"] <- "Dinoflagellata IS"
dat1$Order[dat1$Order == "Coccidiomorphea_X"] <- "Coccidiomorphea IS"
dat1$Phylum[dat1$Phylum == "Bacteria_NA"] <- "Bacteria IS"

my_title1 <- expression(paste("Microbial Orders within ", italic("P. clavata")))

Fig1A <- ggplot(dat1[Abundance > 0], aes(x = factor(Sample, levels=ordered), y = factor(Order, levels=bac_orders))) + geom_point(aes(size = Abundance, fill=Phylum), alpha = 1, shape = 21) + 
  scale_size_continuous(limits = c(0.000001, 100), range = c(0.1,10), breaks = c(1,10,50,75)) + 
  labs( x= "Population", y = "Prokaryotic Order", size = "Relative Abundance %", fill="Prokaryotic Phylum") + theme_bw() +  
  scale_fill_manual(values = c25, breaks=c('Verrucomicrobiota', 'Proteobacteria', 'Firmicutes', 'Cyanobacteria', 'Bacteroidota', 'Bacteria IS', 'Other')) + theme(axis.text.x = element_text(angle = 90, vjust = .5, hjust=1)) + 
  ggtitle(label=my_title1, subtitle = "With median relative abundance above 1%") 
Fig1A
```

## Figure 1B. Bubble Plot of Euk Populations (w/ Portugal)
```{r}
bub <- merge_samples(psf_euk_coral_Tmin, "population") 
type_taxa <- bub %>% 
  tax_glom(taxrank = "Order") %>% 
  transform_sample_counts(function(x) {x/sum(x)*100} )  

type_taxa <- type_taxa %>% 
  psmelt() %>% 
  arrange(Abundance) 


library(data.table)
# create dataframe from phyloseq object
dat <- data.table(type_taxa)
# convert Phylum to a character vector from a factor because R
dat$Order <- as.character(dat$Order)
# group dataframe by Phylum, calculate median rel. abundance
dat[, median := median(Abundance, na.rm = FALSE), 
    by = "Order"]
# Change name to remainder of Phylum less than 2%
dat[(median <= 0.01), Order := "Below Threshold"]
dat[(Order == "Below Threshold"), Division := "Other"]

dat$Order[dat$Order == "Eukaryota_NA"] <- "Eukaryota IS"
dat$Order[dat$Order == "Dinophyceae_NA"] <- "Dinophyceae IS"
dat$Order[dat$Order == "Dinophyceae_X"] <- "Dinophyceae IS"
dat$Order[dat$Order == "Apicomplexa_NA"] <- "Apicomplexa IS"
dat$Order[dat$Order == "Apicomplexa_X"] <- "Apicomplexa IS"
dat$Order[dat$Order == "Alveolata_NA"] <- "Alveolata IS"
dat$Order[dat$Order == "Bacillariophyta_X"] <- "Bacillariophyta IS"
dat$Order[dat$Order == "Syndiniales_X"] <- "Syndiniales IS"
dat$Order[dat$Order == "Dinoflagellata_NA"] <- "Dinoflagellata IS"
dat$Order[dat$Order == "Coccidiomorphea_X"] <- "Coccidiomorphea IS"
dat$Division[dat$Division == "Eukaryota_NA"] <- "Eukaryota IS"

my_title <- expression(paste("Eukaryotic Orders within ", italic("P. clavata")))

Fig1B <- ggplot(dat[Abundance > 0], aes(x = factor(Sample, levels=ordered), y = factor(Order, levels=euk_orders))) + geom_point(aes(size = Abundance, fill=Division), alpha = 1, shape = 21) + 
  scale_size_continuous(limits = c(0.000001, 100), range = c(0.1,10), breaks = c(1,10,50,75)) + 
  labs( x= "Population", y = "Eukaryotic Order", size = "Relative Abundance %", fill="Eukaryotic Division") + theme_bw() +  
  scale_fill_manual(values = palette,breaks=c('Apicomplexa', 'Ciliophora', 'Dinoflagellata', 'Fungi', 'Haptophyta', 'Ochrophyta', 'Eukaryota IS', 'Other')) + 
  theme(axis.text.x = element_text(angle = 90, vjust = .5, hjust=1, face="bold"))
Fig1B
```

### Combine into One Figure
```{r}
library("ggpubr")
Fig1A_x <- Fig1A + theme(axis.title.x = element_blank(),axis.text.x = element_blank())

p <- ggarrange(Fig1A_x, Fig1B, nrow=2, align="v", common.legend = FALSE, legend="right")
p

pdf("Fig1-Populations.pdf", width=7, height=8)
plot(p)
dev.off()
```


## Figure 2. Bubble Plot of Thermal Tolerances
### Proks
```{r}
bub1 <- merge_samples(noport_bac, "resitance_14_21") 
type_taxa1 <- bub1 %>% 
  tax_glom(taxrank = "Order") %>% 
  transform_sample_counts(function(x) {x/sum(x)*100} )  

type_taxa1 <- type_taxa1 %>% 
  psmelt() %>% 
  arrange(Abundance) 


library(data.table)
# create dataframe from phyloseq object
dat1 <- data.table(type_taxa1)
# convert Phylum to a character vector from a factor because R
dat1$Order <- as.character(dat1$Order)
# group dataframe by Phylum, calculate median rel. abundance
dat1[, median := median(Abundance, na.rm = FALSE), 
    by = "Order"]
# Change name to remainder of Phylum less than 2%
dat1[(median <= 0.01), Order := "Below Threshold"]
dat1[(Order == "Below Threshold"), Phylum := "Other"]

dat1$Order[dat1$Order == "Omnitrophia_NA"] <- "Omnitrophia IS"
dat1$Order[dat1$Order == "Gammaproteobacteria_NA"] <- "Gammaproteobacteria IS"
dat1$Order[dat1$Order == "Bacilli_NA"] <- "Bacilli IS"
dat1$Order[dat1$Order == "Bacteria_NA"] <- "Bacteria IS"
dat1$Order[dat1$Order == "Bacillariophyta_X"] <- "Bacillariophyta IS"
dat1$Phylum[dat1$Phylum == "Bacteria_NA"] <- "Bacteria IS"
dat1$Order[dat1$Order == "Alphaproteobacteria_NA"] <- "Alphaproteobacteria IS"

my_title <- expression(paste("Microbial Orders within ", italic("P. clavata")))

Fig2A <- ggplot(dat1[Abundance > 0], aes(x = factor(Sample, levels=c("Hyper Sensitive", "Sensitive", "Tolerant","Resistant", "Super Resistant")), y = factor(Order, levels=bac_orders))) + geom_point(aes(size = Abundance, fill=Phylum), alpha = 1, shape = 21) + 
  scale_size_continuous(limits = c(0.000001, 100), range = c(0.1,10), breaks = c(1,10,50,75)) + 
  labs( x= "Thermal Tolerance", y = "Prokaryotic Order", size = "Relative Abundance %", fill="Prokaryotic Phylum") + theme_bw() +  
  scale_fill_manual(values = c25,breaks=c('Verrucomicrobiota', 'Proteobacteria', 'Firmicutes', 'Cyanobacteria', 'Bacteroidota', 'Bacteria IS', 'Other')) + 
  ggtitle(label=my_title, subtitle = "With median relative abundance above 1%") 
Fig2A
```

### Euks
```{r}
bub <- merge_samples(noport, "resitance_14_21") 
type_taxa <- bub %>% 
  tax_glom(taxrank = "Order") %>% 
  transform_sample_counts(function(x) {x/sum(x)*100} )  

type_taxa <- type_taxa %>% 
  psmelt() %>% 
  arrange(Abundance) 


library(data.table)
# create dataframe from phyloseq object
dat <- data.table(type_taxa)
# convert Phylum to a character vector from a factor because R
dat$Order <- as.character(dat$Order)
# group dataframe by Phylum, calculate median rel. abundance
dat[, median := median(Abundance, na.rm = FALSE), 
    by = "Order"]
# Change name to remainder of Phylum less than 2%
dat[(median <= 0.01), Order := "Below Threshold"]
dat[(Order == "Below Threshold"), Division := "Other"]

dat$Order[dat$Order == "Eukaryota_NA"] <- "Eukaryota IS"
dat$Order[dat$Order == "Dinophyceae_NA"] <- "Dinophyceae IS"
dat$Order[dat$Order == "Dinophyceae_X"] <- "Dinophyceae IS"
dat$Order[dat$Order == "Apicomplexa_NA"] <- "Apicomplexa IS"
dat$Order[dat$Order == "Apicomplexa_X"] <- "Apicomplexa IS"
dat$Order[dat$Order == "Alveolata_NA"] <- "Alveolata IS"
dat$Order[dat$Order == "Bacillariophyta_X"] <- "Bacillariophyta IS"
dat$Order[dat$Order == "Syndiniales_X"] <- "Syndiniales IS"
dat$Order[dat$Order == "Dinoflagellata_NA"] <- "Dinoflagellata IS"
dat$Order[dat$Order == "Coccidiomorphea_X"] <- "Coccidiomorphea IS"
dat$Order[dat$Order == "Phaeophyceae_X"] <- "Phaeophyceae IS"

Fig2B <- ggplot(dat[Abundance > 0], aes(x = factor(Sample, levels=c("Hyper Sensitive", "Sensitive", "Tolerant","Resistant", "Super Resistant")), y = factor(Order, levels=euk_orders))) + geom_point(aes(size = Abundance, fill=Division), alpha = 1, shape = 21) + 
  scale_size_continuous(limits = c(0.000001, 100), range = c(0.1,10), breaks = c(1,10,50,75)) + 
  labs( x= "Thermal Tolerance", y = "Eukaryotic Order", size = "Relative Abundance %", fill="Eukaryotic Division") + theme_bw() +  
  scale_fill_manual(values = palette,breaks=c('Apicomplexa', 'Ciliophora', 'Dinoflagellata', 'Fungi', 'Haptophyta', 'Ochrophyta', 'Eukaryota IS', 'Other')) + 
  theme(axis.text.x = element_text(angle = 40, hjust=1, face="bold"))
Fig2B
```

### Combine into One Figure
```{r}
library("ggpubr")
Fig2A_x <- Fig2A + theme(axis.title.x = element_blank(),axis.text.x = element_blank())

p <- ggarrange(Fig2A_x, Fig2B, nrow=2, heights=c(0.45,0.55), align="v", common.legend = FALSE, legend="right")
p

pdf("Fig2-Resistance.pdf", width=7, height=9)
plot(p)
dev.off()
```


## Figure 3. ANCOM (Euks and Proks, combined levels)
```{r}
library(ANCOMBC)
library(DT)
noport <- subset_samples(psf_euk_coral_Tmin, psf_euk_coral_Tmin@sam_data$region!="Portugal")

notol <- subset_samples(noport, noport@sam_data$resitance_14_21!="Tolerant")
# Re-code groups so that all resistance or together
sample_data(notol)$resitance_14_21 = recode(sample_data(notol)$resitance_14_21,
                                  "Hyper Sensitive" = "Sensitive",
                                  "Sensitive" = "Sensitive",
                                  "Resistant" = "Resistant",
                                  "Super Resistant" = "Resistant")


# Aggregate to phylum level

oldtax <- data.frame(tax_table(notol))

oldtax$Order[oldtax$Order == "Dinophyceae_X"] <- "Dinophyceae IS"
oldtax$Order[oldtax$Order == "Prymnesiophyceae_X"] <- "Prymnesiophyceae IS"
oldtax$Order[oldtax$Order == "Prasino-Clade-9_NA"] <- "Prasino-Clade-9 IS"
oldtax$Order[oldtax$Order == "Apicomplexa_X"] <- "Apicomplexa IS"
oldtax$Order[oldtax$Order == "Dinoflagellata_X"] <- "Dinoflagellata IS"
oldtax$Order[oldtax$Order == "Coccidiomorphea_NA"] <- "Coccidiomorphea IS"
oldtax$Order[oldtax$Order == "Alveolata_X"] <- "Alveolata IS"
oldtax$Order[oldtax$Order == "Dinophyceae_NA"] <- "Dinophyceae IS"
oldtax$Order[oldtax$Order == "Eukaryota_X"] <- "Eukaryota IS"
oldtax$Order[oldtax$Order == "Dinophyceae_NA"] <- "Dinophyceae IS"
oldtax$Order[oldtax$Order == "Prymnesiophyceae_NA"] <- "Prymnesiophyceae IS"
oldtax$Order[oldtax$Order == "Prasino-Clade-9_X"] <- "Prasino-Clade-9 IS"
oldtax$Order[oldtax$Order == "Apicomplexa_NA"] <- "Apicomplexa IS"
oldtax$Order[oldtax$Order == "Dinoflagellata_NA"] <- "Dinoflagellata IS"
oldtax$Order[oldtax$Order == "Coccidiomorphea_X"] <- "Coccidiomorphea IS"
oldtax$Order[oldtax$Order == "Alveolata_NA"] <- "Alveolata IS"
oldtax$Order[oldtax$Order == "Dinophyceae_X"] <- "Dinophyceae IS"
oldtax$Order[oldtax$Order == "Eukaryota_NA"] <- "Eukaryota IS"
oldtax$Order[oldtax$Order == "Phyllopharyngea_NA"] <- "Phyllopharyngea IS"
oldtax$Order[oldtax$Order == "Syndiniales_X"] <- "Syndiniales IS"
oldtax$Order[oldtax$Order == "Syndiniales_NA"] <- "Syndiniales IS"

tax_table(notol) <- as.matrix(oldtax)
genus_data = aggregate_taxa(notol, "Order")

out = ancombc(phyloseq = genus_data, formula = "resitance_14_21", 
              p_adj_method = "none", zero_cut = 0.90, lib_cut = 0, 
              group = "resitance_14_21", struc_zero = TRUE, neg_lb = TRUE, tol = 1e-5, 
              max_iter = 100, conserve = TRUE, alpha = 0.05, global = TRUE)

res = out$res
res_global = out$res_global

tab_diff = res$diff_abn
tab_diff %>% 
  datatable(caption = "Differentially Abundant Taxa 
            from the Primary Result")

samp_frac = out$samp_frac
# Replace NA with 0
samp_frac[is.na(samp_frac)] = 0 

# Add pesudo-count (1) to avoid taking the log of 0
log_obs_abn = log(abundances(genus_data) + 1) 
# Adjust the log observed abundances
log_obs_abn_adj = t(t(log_obs_abn) - samp_frac)
# Show the first 6 samples
round(log_obs_abn_adj[, 1:6], 2) %>% 
  datatable(caption = "Bias-adjusted log observed abundances")


df_fig1 = data.frame(res$beta * res$diff_abn, check.names = FALSE) %>% 
  rownames_to_column("taxon_id")
df_fig2 = data.frame(res$se * res$diff_abn, check.names = FALSE) %>% 
  rownames_to_column("taxon_id")
colnames(df_fig2)[-1] = paste0(colnames(df_fig2)[-1], "SD")
df_fig = df_fig1 %>% left_join(df_fig2, by = "taxon_id") %>%
  transmute(taxon_id, resitance_14_21Sensitive, resitance_14_21SensitiveSD) %>% 
  filter(resitance_14_21Sensitive != 0) %>% arrange(desc(resitance_14_21Sensitive)) %>%
  mutate(group = ifelse(resitance_14_21Sensitive > 0, "g1", "g2"))
df_fig$taxon_id = factor(df_fig$taxon_id, levels = df_fig$taxon_id)
  
ANCOM_EUK = ggplot(data = df_fig, 
           aes(x = taxon_id, y = resitance_14_21Sensitive, fill = resitance_14_21Sensitive, color = resitance_14_21Sensitive)) + 
  geom_bar(stat = "identity", width = 0.7, 
           position = position_dodge(width = 0.4)) + scale_fill_viridis_c(option = "plasma") + scale_color_viridis_c(option = "plasma") +
  geom_errorbar(aes(ymin = resitance_14_21Sensitive - resitance_14_21SensitiveSD, ymax = resitance_14_21Sensitive + resitance_14_21SensitiveSD), width = 0.2,
                position = position_dodge(0.05), color = "black") + 
  labs(x = "Eukaryotic Order", y = "Log fold change") + 
  theme_bw() + 
  theme(legend.position = "none",
        panel.grid.minor.y = element_blank()) + coord_flip() + scale_y_continuous(limits = c(-3, 3))
ANCOM_EUK
```
```{r}
library(ANCOMBC)
library(DT)

noport_bac <- subset_samples(psf_bac_coral_Tmin, psf_bac_coral_Tmin@sam_data$region!="Portugal")

notol <- subset_samples(noport_bac, noport_bac@sam_data$resitance_14_21!="Tolerant")

sample_data(notol)$resitance_14_21 = recode(sample_data(notol)$resitance_14_21,
                                  "Hyper Sensitive" = "Sensitive",
                                  "Sensitive" = "Sensitive",
                                  "Resistant" = "Resistant",
                                  "Super Resistant" = "Resistant")


# Aggregate to phylum level

oldtax <- data.frame(tax_table(notol))

oldtax$Order[oldtax$Order == "Gammaproteobacteria_NA"] <- "Gammaproteobacteria IS"
oldtax$Order[oldtax$Order == "Alphaproteobacteria_NA"] <- "Alphaproteobacteria IS"
oldtax$Order[oldtax$Order == "Bacteria_NA"] <- "Bacteria IS"

tax_table(notol) <- as.matrix(oldtax)
genus_data = aggregate_taxa(notol, "Order")

out = ancombc(phyloseq = genus_data, formula = "resitance_14_21", 
              p_adj_method = "none", zero_cut = 0.90, lib_cut = 0, 
              group = "resitance_14_21", struc_zero = TRUE, neg_lb = TRUE, tol = 1e-5, 
              max_iter = 100, conserve = TRUE, alpha = 0.05, global = TRUE)

res = out$res
res_global = out$res_global

samp_frac = out$samp_frac
# Replace NA with 0
samp_frac[is.na(samp_frac)] = 0 

# Add pesudo-count (1) to avoid taking the log of 0
log_obs_abn = log(abundances(genus_data) + 1) 
# Adjust the log observed abundances
log_obs_abn_adj = t(t(log_obs_abn) - samp_frac)
# Show the first 6 samples
round(log_obs_abn_adj[, 1:6], 2) %>% 
  datatable(caption = "Bias-adjusted log observed abundances")


df_fig1 = data.frame(res$beta * res$diff_abn, check.names = FALSE) %>% 
  rownames_to_column("taxon_id")
df_fig2 = data.frame(res$se * res$diff_abn, check.names = FALSE) %>% 
  rownames_to_column("taxon_id")
colnames(df_fig2)[-1] = paste0(colnames(df_fig2)[-1], "SD")
df_fig = df_fig1 %>% left_join(df_fig2, by = "taxon_id") %>%
  transmute(taxon_id, resitance_14_21Sensitive, resitance_14_21SensitiveSD) %>% 
  filter(resitance_14_21Sensitive != 0) %>% arrange(desc(resitance_14_21Sensitive)) %>%
  mutate(group = ifelse(resitance_14_21Sensitive > 0, "g1", "g2"))
df_fig$taxon_id = factor(df_fig$taxon_id, levels = df_fig$taxon_id)
  
ANCOM_BAC = ggplot(data = df_fig, 
           aes(x = taxon_id, y = resitance_14_21Sensitive, fill = resitance_14_21Sensitive, color = resitance_14_21Sensitive)) + 
  geom_bar(stat = "identity", width = 0.7, 
           position = position_dodge(width = 0.4)) + scale_fill_viridis_c(option = "plasma") + scale_color_viridis_c(option = "plasma") +
  geom_errorbar(aes(ymin = resitance_14_21Sensitive - resitance_14_21SensitiveSD, ymax = resitance_14_21Sensitive + resitance_14_21SensitiveSD), width = 0.2,
                position = position_dodge(0.05), color = "black") + 
  labs(x = "Prokaryotic Order", y = "Log fold change", 
       title = "Log Fold Change in ANCOM Significant Taxa: Sensitive vs Resistant") + 
  theme_bw() + 
  theme(legend.position = "none",
        panel.grid.minor.y = element_blank()) + coord_flip() + scale_y_continuous(limits = c(-3, 3))
ANCOM_BAC
```
```{r}
library("ggpubr")

p <- ggarrange(ANCOM_BAC, ANCOM_EUK, nrow=2, align="v", heights=c(0.45, 0.55), common.legend = FALSE, legend="none")
p

pdf("Fig3-ANCOM-LFC.pdf", width=8, height=8)
plot(p)
dev.off()
```
## Figure 4. Corallicolid Tree (Populations)
###Extract ASVs (kept 16)
```{r}
mergedGP <- subset_taxa(noport, Division=="Apicomplexa")
f1<- filterfun_sample(topf(0.50)) # keep ASV reads only if they are in the most abundant 50% of Dinos in at least 1 of the samples in dataset
wh1 <- genefilter_sample(mergedGP, f1, A=2)
mergedGP2 <- prune_taxa(wh1, mergedGP)
df <- data.frame(mergedGP2@tax_table)

write.csv(rownames(df), "/Volumes/projects/bonacolta/pcla/paramuricea_eukaryome/new/analysis/trees/Api/Api_ASVs.csv")
# Correct Sheet so that only ASVs are listed
"/Volumes/projects/bonacolta/pcla/paramuricea_eukaryome/new/analysis/trees/Api/Api_ASVs.txt"
```
```{bash}
cd /Volumes/projects/bonacolta/pcla/paramuricea_eukaryome/new/analysis/trees/Api/

grep -w -A 1 -f  Api_ASVs.txt ../ASVs.fa | grep -v -- "^--$" > pcla_Api_ASVs.fa

hmmalign -o pcla_Api_epa_alignment.sto --dna --mapali coralicollids_seqdump.aligned.fa coralicollids.hmm pcla_Api_ASVs.fa

perl ~/Desktop/scripts/stockholm2fasta.pl pcla_Api_epa_alignment.sto > pcla_Api_epa_alignment.fa
#pcla_Api_epa_alignment.fixed.fa

raxmlHPC-PTHREADS -T 4 -m GTRCAT -f v -G 0.2 -n pcla_apis_epa -s pcla_Api_epa_alignment.fixed.fa -t RAxML_bestTree.coralicollids_seqdump

sed 's/QUERY___//g' RAxML_labelledTree.pcla_apis_epa | sed 's/\[I[0-9]*\]//g' > RAxML_placement_tree_pcla_Api.tre
```
```{r}
noport <- subset_samples(psf_euk_coral_Tmin, psf_euk_coral_Tmin@sam_data$region!="Portugal")
mergedGP <- noport %>% merge_samples("population")
ASVs <- read.delim("/Volumes/projects/bonacolta/pcla/paramuricea_eukaryome/new/analysis/trees/Api/Api_ASVs.txt", header=FALSE)
ASVs  <- ASVs  %>% pull(V1)
my_subset <- subset(t(mergedGP@otu_table@.Data), rownames(t(mergedGP@otu_table@.Data)) %in% ASVs)
my_subset1 <- phyloseq(otu_table(my_subset, taxa_are_rows=TRUE))
mergedGP <- merge_phyloseq(my_subset1, mergedGP@tax_table, mergedGP@sam_data)
mergedGP <- mergedGP %>%  transform_sample_counts(function(x) {x/sum(x)*100} )
tr <- read.tree("/Volumes/projects/bonacolta/pcla/paramuricea_eukaryome/new/analysis/trees/Api/RAxML_placement_tree_pcla_Api.tre")
#Made TXT with annotated names plus all the ASVS
new_tips <- read.delim("/Volumes/projects/bonacolta/pcla/paramuricea_eukaryome/new/analysis/trees/Api/tree_anno.txt", header = TRUE)
tr <- sub.taxa.label(tr, new_tips)
tr <- drop.tip(tr, c("KT806396_Outgroup", "KT806398_Outgroup", "GU825688_Outgroup", NA), trim.internal = TRUE)
tr<- root(tr, outgroup ="KF579890_Corallicolidae_COR6_sp.")

spec <- tax_table(mergedGP) %>% data.frame(stringsAsFactors = FALSE) %>% tibble::rownames_to_column("otu")
p <- ggtree(tr, branch.length = "y", scale=0.09) %<+% spec 

#flip node 74
#p <- flip(p, 76, 75)

gd <- p$data
melt_data<- psmelt(mergedGP)

tt <- melt_data %>% left_join(select(gd,OTU=label,x,y),by="OTU") %>%
  arrange(factor(Sample, levels=ordered)) %>%  mutate(sample2=factor(Sample,levels=unique(Sample)),
  col=as.numeric(sample2),x.col=scales::rescale(col,to=c(.23,.405)))
#g <- p + geom_tiplab(size = 2, align=TRUE, linesize=.25)  + geom_treescale(x=0.05, y=0, offset=0.2, fontsize = 2.5)  +
#  geom_tile(data=tt,aes(x=x.col,y=y,fill=factor(Sample, levels = coral_order),alpha=Abundance)) + 
#  theme(legend.position="right", plot.title = element_text(size = 15, face = "bold", hjust = 0.5), legend.title=element_text(size=10, face="bold"), legend.text=element_text(size=8))  + ggtitle("Apicomplexa ASVs between Cnidarian Families") +
#  scale_alpha_continuous(limits=c(0.001,100),na.value=0, range = c(0.25, 1)) + scale_fill_manual(values=c25) +scale_colour_viridis_d(option="magma") +
#  labs(fill="Cnidarian Family", alpha= "Relative Abundance") +
#  theme(panel.grid.major.y=element_line(), panel.grid.minor.y=element_line())
#g


##Changing heatmap
g <- p + geom_tiplab(size = 4, align=TRUE, linesize=.20, hjust="right", offset=0.16, linetype=NA)  + geom_treescale(x=0.05, y=-0.5, offset=0.2, fontsize = 2.5)  +
  geom_tile(data=tt,aes(x=x.col,y=y,fill=Abundance)) + 
  theme(legend.position="right", plot.title = element_text(size = 15, face = "bold", hjust = 0.5), legend.title=element_text(size=10, face="bold"), legend.text=element_text(size=8)) +
  labs(fill="Relative Abundance") + scale_fill_gradient2(low="transparent", high = "#3182bd", mid= "#deebf7",midpoint= 5,limits=c(0.0001, 100), na.value="transparent") +
  scale_y_continuous(minor_breaks = seq(1 , 52, 1), breaks = seq(1, 52, 1), expand = c(0.013, 1)) +  scale_x_continuous(minor_breaks = seq(0.23 , .405, 0.0175), breaks = seq(0.23 , .405, 0.0175)) +
  theme(panel.grid.major.x=element_line(size = (0.2), colour="lightgrey"), panel.grid.minor.x=element_line(size = (0.2), colour="grey"), axis.title.y = element_blank())
g
g$data
## Combine again at OTU the use this reads plot.
#Bar Plot
mergedGP2 <- noport %>% merge_samples("time")

my_subsett <- subset(t(mergedGP2@otu_table@.Data), rownames(t(mergedGP2@otu_table@.Data)) %in% ASVs)
my_subsett1 <- phyloseq(otu_table(my_subsett, taxa_are_rows=TRUE))
mergedGP2 <- merge_phyloseq(my_subsett1, mergedGP2@tax_table, mergedGP2@sam_data)

glom <- mergedGP2  %>%  transform_sample_counts(function(x) {x/sum(x)*100} )
glom # should list # taxa as # phyla
data <- psmelt(glom) # create dataframe from phyloseq object
#data$Order <- as.character(data$Order) #convert to character
ttt <- g$data
ttt <- ttt[with(ttt, order(+y)), ]
target <- as.vector(ttt$label)
tttt <- ttt[!duplicated(ttt["label"]), ]
names(tttt)[names(tttt) == "label"] <- "OTU"
data2 <- merge(data, tttt, by='OTU')
data3 <- data2[data2$Abundance != "NaN", ] 
# Add Accession names to Data3
as <- ttt[!grepl("ASV", ttt$label),]
as <- as[!is.na(as$label), ]
ass <- as.vector(as$label)
data4 <- data3 %>% add_row(OTU=ass)
library(gdata)

data4 <- data4[order(match(data4$OTU, target)), , drop = FALSE]
# Add Sample count per OTU
mergedGP2
## This object has all the info. I want to extract OTU Table. Then Count how many columns have a number greater than 0. I will export thi snumber and graph it.
df <- noport@otu_table@.Data
df <- data.frame(df)
df$sample_count <- apply(df[, grep("", names(df))], MARGIN = 1, 
                function(x) sum(x > 0, na.rm = T))
df$sample_total <- apply(df[, grep("", names(df))], MARGIN = 1, 
                function(x) sum(x >= 0, na.rm = T))
df$sample_percent <- df$sample_count / df$sample_total *100




df2 <- subset(df, row.names(df) %in% target)

#Need to add in Labels here to DF2 
newlist <- grep(pattern = 'ASV', x = target, value=TRUE, invert=TRUE)
newlist[!is.na(newlist)]
empty <- data.frame(newlist[!is.na(newlist)])  
empty <- empty %>% add_column(new_col = NA)
newcol <- empty[,1]
rownames(empty) <- newcol

df2 <- dplyr::bind_rows(df2, empty)

df2 <- df2[order(match(rownames(df2), target)), , drop = FALSE]

#Match Samples then add zeroes for not listed
samples <- as.vector(df2$sample_percent)
data4$sample_percent=samples
library(reshape2)

b <- ggplot(data=data4, aes(x=y, y=Abundance, na.rm = TRUE)) + theme_classic() + geom_bar(stat="identity", fill = "#55C667FF") + coord_flip() +
      theme(axis.title.y = element_blank(), axis.text.y = element_blank(), axis.text.x= element_text(size=5), axis.title.x= element_text(size=9)) + scale_y_continuous(expand = c(0, 0), na.value=0, position = "right", breaks=c(0, 25, 50)) + guides(fill=guide_legend(title="Value")) + ylab("Relative Abundance (%)") +
  scale_x_continuous(expand = c(0.0, 0), na.value=0, limits=c(-1.8,32.5))

b
c <- ggplot(data=data4, aes(x=y, y=sample_percent, na.rm = TRUE)) + theme_classic() + geom_bar(stat="identity", fill = "#482677FF") + coord_flip() +
      theme(axis.title.y = element_blank(), axis.text.y = element_blank(), axis.text.x= element_text(size=5), axis.title.x= element_text(size=9)) + scale_y_continuous(expand = c(0, 0), na.value=0, position = "right", breaks=c(0,50,100)) + guides(fill=guide_legend(title="Value")) + ylab("Sample Prevalence (%)") +
  scale_x_continuous(expand = c(0.0, 0), na.value=0, limits=c(-1.8,32.5))

c
library(ggpubr)
a<- ggarrange(b, c, ncol=2, nrow=1, align = "h", common.legend = TRUE, legend="right") 

z <- ggarrange(g, a, ncol=2, nrow=1, widths = c(0.8,.40), align = "v", common.legend = TRUE, legend="right")
z
zz <- annotate_figure(z, fig.lab = "Heatmap of Corallicolid ASVs across Sampling Locations", fig.lab.face = "bold", fig.lab.size = 14, fig.lab.pos = "top.left")

pdf("Fig4-ApiTree.pdf", width=12, height=6)
plot(zz)
dev.off()
```
## Figure 5. Combined SPARCC Network Plot
- Network Analysis between domains
- I need to extract sample names from psf_euk_coral_Tmin and grep out the "E-" then re-add the sample names.
```{r}
euk_names_fixed <- c("2-1-10-T-minus-1", "2-1-5-T-minus-1", "2-1-6-T-minus-1", "2-1-8-T-minus-1", "2-2-2-T-minus-1", "2-2-4-T-minus-1", "2-2-9-T-minus-1","3-1-1-T-minus-1", "3-1-2-T-minus-1", "3-1-3-T-minus-1", "3-1-6-T-minus-1", "3-3-1-T-minus-1", "3-3-3-T-minus-1", "3-3-4-T-minus-1", "8-4-1-T-minus-1", "8-4-4-T-minus-1", "8-4-9-T-minus-1", "8-5-10-T-minus-1", "8-5-5-T-minus-1", "pop1-1", "pop1-10", "pop1-2", "pop1-3", "pop1-4", "pop1-5", "pop1-6", "pop1-7", "pop1-8", "pop1-9", "pop10-1", "pop10-10", "pop10-2", "pop10-3", "pop10-4", "pop10-5", "pop10-6", "pop10-7", "pop10-8", "pop10-9", "pop11-1", "pop11-10", "pop11-2", "pop11-3", "pop11-4", "pop11-5", "pop11-6", "pop11-7", "pop11-8", "pop11-9", "pop12-1", "pop12-10", "pop12-2", "pop12-3", "pop12-4", "pop12-5", "pop12-6", "pop12-7", "pop12-8", "pop2-1", "pop2-10", "pop2-2", "pop2-3", "pop2-4", "pop2-5", "pop2-6", "pop2-7", "pop2-8", "pop2-9", "pop3-1", "pop3-10", "pop3-2", "pop3-3", "pop3-4", "pop3-5", "pop3-6", "pop3-7", "pop3-8", "pop3-9", "pop4-1", "pop4-10", "pop4-2", "pop4-3", "pop4-4", "pop4-5", "pop4-6", "pop4-7", "pop4-8", "pop4-9", "pop5-1", "pop5-10", "pop5-2", "pop5-3", "pop5-4", "pop5-5", "pop5-6", "pop5-7", "pop5-8", "pop5-9", "pop6-1", "pop6-10", "pop6-2", "pop6-3", "pop6-4", "pop6-5", "pop6-6", "pop6-7", "pop6-8", "pop6-9", "pop7-1", "pop7-10", "pop7-2", "pop7-3", "pop7-4", "pop7-5", "pop7-6", "pop7-7", "pop7-8", "pop7-9", "pop8-1", "pop8-10", "pop8-2", "pop8-3", "pop8-4", "pop8-5", "pop8-6", "pop8-7", "pop8-8", "pop8-9", "pop9-1", "pop9-10", "pop9-2", "pop9-3", "pop9-4", "pop9-5", "pop9-6", "pop9-7", "pop9-8", "pop9-9")
euk_names_fixed

sample_names(psf_euk_coral_Tmin) <- euk_names_fixed
sample_names(psf_euk_coral_Tmin)
```

- Then keep only samples found in psf_bac_coral_Tmin,
```{r}
subset_samps <- c("2-1-5-T-minus-1" , "3-1-6-T-minus-1" , "3-3-4-T-minus-1" , "pop1-1" , "pop1-10" , "pop1-2" , "pop1-3" , "pop1-4" , "pop1-6" , "pop1-7" , "pop1-8" , "pop1-9" , "pop10-1" , "pop10-10" , "pop10-2" , "pop10-3" , "pop10-4" , "pop10-5" , "pop10-6" , "pop10-7" , "pop10-8" , "pop10-9" , "pop11-1" , "pop11-10" , "pop11-2" , "pop11-3" , "pop11-4" , "pop11-5" , "pop11-6" , "pop11-7" , "pop11-8" , "pop11-9" , "pop12-5" , "pop2-4" , "pop2-5" , "pop3-4" , "pop4-1" , "pop4-10" , "pop4-2" , "pop4-3" , "pop4-4" , "pop4-6" , "pop4-7" , "pop4-8" , "pop4-9" , "pop5-1" , "pop5-10" , "pop5-2" , "pop5-3" , "pop5-4" , "pop5-5" , "pop5-6" , "pop5-8" , "pop5-9" , "pop6-1" , "pop6-10" , "pop6-2" , "pop6-3" , "pop6-4" , "pop6-5" , "pop6-6" , "pop6-7" , "pop6-8" , "pop6-9" , "pop7-1" , "pop7-10" , "pop7-2" , "pop7-3" , "pop7-4" , "pop7-5" , "pop7-6" , "pop7-7" , "pop7-8" , "pop7-9" , "pop8-2" , "pop8-3" , "pop8-4" , "pop8-5" , "pop8-6" , "pop8-7" , "pop8-8" , "pop8-9" , "pop9-1" , "pop9-10" , "pop9-2" , "pop9-4" , "pop9-5" , "pop9-6" , "pop9-7" , "pop9-8" , "2-1-5-T-minus-1" , "3-1-6-T-minus-1" , "3-3-4-T-minus-1" , "pop1-1" , "pop1-10" , "pop1-2" , "pop1-3" , "pop1-4" , "pop1-6" , "pop1-7" , "pop1-8" , "pop1-9" , "pop10-1" , "pop10-10" , "pop10-2" , "pop10-3" , "pop10-4" , "pop10-5" , "pop10-6" , "pop10-7" , "pop10-8" , "pop10-9" , "pop11-1" , "pop11-10" , "pop11-2" , "pop11-3" , "pop11-4" , "pop11-5" , "pop11-6" , "pop11-7" , "pop11-8" , "pop11-9" , "pop12-5" , "pop2-4" , "pop2-5" , "pop3-4" , "pop4-1" , "pop4-10" , "pop4-2" , "pop4-3" , "pop4-4" , "pop4-6" , "pop4-7" , "pop4-8" , "pop4-9" , "pop5-1" , "pop5-10" , "pop5-2" , "pop5-3" , "pop5-4" , "pop5-5" , "pop5-6" , "pop5-8" , "pop5-9" , "pop6-1" , "pop6-10" , "pop6-2" , "pop6-3" , "pop6-4" , "pop6-5" , "pop6-6" , "pop6-7" , "pop6-8" , "pop6-9" , "pop7-1" , "pop7-10" , "pop7-2" , "pop7-3" , "pop7-4" , "pop7-5" , "pop7-6" , "pop7-7" , "pop7-8" , "pop7-9" , "pop8-2" , "pop8-3" , "pop8-4" , "pop8-5" , "pop8-6" , "pop8-7" , "pop8-8" , "pop8-9" , "pop9-1" , "pop9-10" , "pop9-2" , "pop9-4" , "pop9-5" , "pop9-6" , "pop9-7" , "pop9-8")

network_bac <- prune_samples(subset_samps, psf_bac_coral_Tmin)
network_euk <- prune_samples(subset_samps, psf_euk_coral_Tmin)
sample_names(network_euk)
sample_names(network_bac)


merged_network <- merge_phyloseq(network_euk, network_bac)
merged_network
network_bac
network_euk
```

```{r}
library(chorddiag)
library(htmlwidgets)
library(circlize)
library(webshot)
library("microeco")
library("file2meco")
library(rgexf)
library(NetCoMi)
library(igraph)
library(chorddiag)
```

```{r}
tax.clean <- data.frame(tax_table(merged_network))
tax.clean$Family[tax.clean$Family == "Dinophyceae_NA"] <- "Dinophyceae IS"
tax.clean$Family[tax.clean$Family == "Dinophyceae_XX"] <- "Dinophyceae IS"
tax.clean$Family[tax.clean$Family == "Apicomplexa_NA"] <- "Apicomplexa IS"
tax_table(merged_network) <- as.matrix(tax.clean)

meco_dataset <- phyloseq2meco(merged_network)
meco_dataset

#t1 <- trans_network$new(dataset = meco_dataset, cal_cor = "SparCC", taxa_level = "OTU", filter_thres = 0.00001, SparCC_simu_num = 100)
t1$cal_network(network_method="SpiecEasi", p_thres = 0.05)

#t1network <- t1$cal_network(network_method="SpiecEasi", p_thres = 0.1)
#t1$save_network(filepath = "/Volumes/GoogleDrive/.shortcut-targets-by-id/1NZWDX6hj2iMLlcMpeA9ILkNyhxyngfoM/Bonacolta\ et\ al.\ 2020\ Paramuricea/paramuricea_microbiome/Figures/Manuscript/ISEP/network_genus.gexf")
# Open in Gephi and save as gexf again, then continue below
#gexf1 <- read.gexf("/Volumes/projects/bonacolta/coral_euks/analysis/network/network_working.gexf")
#igraph1 <- gexf.to.igraph(gexf1)

t1$cal_network_attr()
#t1$cal_node_type()
#t1$plot_taxa_roles(use_type = 1)
t1$cal_eigen()
t1$cal_sum_links(taxa_level = "Family")
t1$plot_sum_links(plot_pos = TRUE, plot_num = 10) # Plot_pos is true, so positive linkages ar eplotted. 

p <- t1$plot_sum_links(plot_pos = TRUE, plot_num = 20)
p$x$option

mat3 = p$x$matrix

for(cn in intersect(rownames(mat3), colnames(mat3))) {
    mat3[cn, cn] = 0
}

chord <- chorddiag(mat3, groupColors=palette, groupnameFontsize=10, margin=155, showTicks=FALSE, groupnamePadding = 10)
chord


save_html(chord, "/Volumes/GoogleDrive/.shortcut-targets-by-id/1NZWDX6hj2iMLlcMpeA9ILkNyhxyngfoM/Bonacolta\ et\ al.\ 2020\ Paramuricea/paramuricea_microbiome/Figures/Manuscript/Network_10082021.html")

save(chord, file="/Volumes/GoogleDrive/.shortcut-targets-by-id/1NZWDX6hj2iMLlcMpeA9ILkNyhxyngfoM/Bonacolta\ et\ al.\ 2020\ Paramuricea/paramuricea_microbiome/Figures/Manuscript/Network_10082021.rds")

save(t1, file="/Volumes/GoogleDrive/.shortcut-targets-by-id/1NZWDX6hj2iMLlcMpeA9ILkNyhxyngfoM/Bonacolta\ et\ al.\ 2020\ Paramuricea/paramuricea_microbiome/Figures/Manuscript/Network_10082021_t1.rds")
```

## Fig 2S. Obligatory Water Sample
```{r}
psf_bac_nofood <- subset_samples(psf_bac, psf_bac@sam_data$type!='food')
mergedGP = merge_samples(psf_bac_nofood, "type")

type_taxa <- mergedGP %>% 
  tax_glom(taxrank = "Order") %>% 
  transform_sample_counts(function(x) {x/sum(x)} ) %>% 
  psmelt() %>% 
  arrange(Order) 

# create dataframe from phyloseq object
dat <- data.table(type_taxa)
# convert Class to a character vector from a factor because R
dat$Order <- as.character(dat$Order)
# group dataframe by Class, calculate median rel. abundance
dat[, median := median(Abundance, na.rm = FALSE), 
    by = "Order"]
# Change name to remainder of Phylum less than 2%
dat[(median <= 0.01), Order := "Below Threshold"]
dat[(median <= 0.10), Phylum := "Other"]

water_bac <- ggplot(dat, aes(x = Sample, y = Abundance, fill = Order)) + 
  geom_bar(stat = "identity") +
  scale_fill_manual(values=c25) +
  guides(fill = guide_legend(reverse = TRUE, keywidth = 1, keyheight = 1)) +
  ylab("Relative Abundance \n") +
  ggtitle("Prokaryotic Order Composition By Sample Type") + scale_y_continuous(limits = c(0,1), expand = c(0,0)) + theme_classic()


##Euks 
psf_euk_nofood <- subset_samples(psf_euk, psf_euk@sam_data$type!='food')
mergedGP1 = merge_samples(psf_euk_nofood, "type")

type_taxa1 <- mergedGP1 %>% 
  tax_glom(taxrank = "Order") %>% 
  transform_sample_counts(function(x) {x/sum(x)} ) %>% 
  psmelt() %>% 
  arrange(Order) 

# create dataframe from phyloseq object
dat1 <- data.table(type_taxa1)
# convert Class to a character vector from a factor because R
dat1$Order <- as.character(dat1$Order)
# group dataframe by Class, calculate median rel. abundance
dat1[, median := median(Abundance, na.rm = FALSE), 
    by = "Order"]
# Change name to remainder of Phylum less than 2%
dat1[(median <= 0.01), Order := "Below Threshold"]
dat1[(median <= 0.10), Division := "Other"]

water_euk <- ggplot(dat1, aes(x = Sample, y = Abundance, fill = Order)) + 
  geom_bar(stat = "identity") +
  scale_fill_manual(values=palette) +
  guides(fill = guide_legend(reverse = TRUE, keywidth = 1, keyheight = 1)) +
  ylab("Relative Abundance \n") +
  ggtitle("Eukaryotic Order Composition By Sample Type") + scale_y_continuous(limits = c(0,1), expand = c(0,0)) + theme_classic()



library("ggpubr")
pdf("Fig2S-Water.pdf", width=9, height=9)
ggarrange(water_bac,water_euk,align = "v",  nrow=2, common.legend = FALSE, legend="right")
dev.off()
```









## Fig 3S & 4S. Diversity Plots Combined
```{r}
library(microbiome)
library(ggpubr)
library(knitr)
library(dplyr)

ad <- prune_taxa(taxa_sums(noport) > 0, noport)
tab <- microbiome::alpha(ad, index = "shannon")
kable(head(tab))

ps1.meta <- meta(ad)
kable(head(ps1.meta))
ps1.meta$Shannon <- tab$diversity_shannon 

# create a list of pairwise comaprisons
fam <- unique(ps1.meta$region) # get the variables


# make a pairwise list that we want to compare.
fam.pairs <- combn(seq_along(fam), 2, simplify = FALSE, FUN = function(i)fam[i])

print(fam.pairs)

#ps1.meta$'' <- alpha(ps1, index = 'shannon')
p1 <- ggboxplot(ps1.meta, x = "region", y = "Shannon",
 add = "boxplot", fill = "region", order = c("Medes ", "Scandola", "Portofino", "Croatia")) + theme_classic() + theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) + scale_fill_viridis_d() + 
  labs(fill='Region', title="Shannon-Wiener Alpha Diversity of Eukaryome", x="Region", y="Shannon-Wiener Diversity Index") + ylim(0,8)

p1 <- p1 + stat_compare_means(comparisons = fam.pairs) 
print(p1)


ad2 <- prune_taxa(taxa_sums(noport_bac) > 0, noport_bac)
tab2 <- microbiome::alpha(ad2, index = "shannon")
kable(head(tab2))
ps1.meta2 <- meta(ad2)
kable(head(ps1.meta))
ps1.meta2$Shannon <- tab2$diversity_shannon 
# create a list of pairwise comaprisons
fam2 <- unique(ps1.meta2$region) # get the variables
# make a pairwise list that we want to compare.
fam.pairs2 <- combn(seq_along(fam2), 2, simplify = FALSE, FUN = function(i)fam2[i])
print(fam.pairs2)
#ps1.meta$'' <- alpha(ps1, index = 'shannon')
p2 <- ggboxplot(ps1.meta2, x = "region", y = "Shannon",
 add = "boxplot", fill = "region", order = c("Medes ", "Scandola", "Portofino", "Croatia")) + theme_classic() + theme(axis.text.x = element_text(angle = 45, hjust = 1)) + scale_fill_viridis_d() + 
  labs(fill='Region', title="Shannon-Wiener Alpha Diversity of Prokaryome", x="Region", y="Shannon-Wiener Diversity Index") + ylim(0,8)
p2 <- p2 + stat_compare_means(comparisons = fam.pairs2) 
print(p2)

p3 <- ggarrange(p2, p1, nrow=2, align="v",legend="none")

p3


pdf("Fig3S_Alpha_region.pdf", width=4, height=8)
plot(p3)
dev.off()
```

### Fig 3S- Alphas
```{r}
library(microbiome)
library(ggpubr)
library(knitr)
library(dplyr)

ad <- prune_taxa(taxa_sums(noport) > 0, noport)
tab <- microbiome::alpha(ad, index = "shannon")
kable(head(tab))

ps1.meta <- meta(ad)
kable(head(ps1.meta))
ps1.meta$Shannon <- tab$diversity_shannon 

# create a list of pairwise comaprisons
fam <- unique(ps1.meta$resitance_14_21) # get the variables


# make a pairwise list that we want to compare.
fam.pairs <- combn(seq_along(fam), 2, simplify = FALSE, FUN = function(i)fam[i])

print(fam.pairs)

#ps1.meta$'' <- alpha(ps1, index = 'shannon')
p1 <- ggboxplot(ps1.meta, x = "resitance_14_21", y = "Shannon",
 add = "boxplot", fill = "resitance_14_21", order = c("Hyper Sensitive", "Sensitive", "Tolerant","Resistant", "Super Resistant")) + theme_classic() + theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) + scale_fill_viridis_d() + 
  labs(fill='Thermal Tolerance', title="Shannon-Wiener Alpha Diversity of Eukaryome", x="Region", y="Shannon-Wiener Diversity Index") + ylim(0,8)

p1 <- p1 + stat_compare_means(comparisons = fam.pairs) 
print(p1)


ad2 <- prune_taxa(taxa_sums(noport_bac) > 0, noport_bac)
tab2 <- microbiome::alpha(ad2, index = "shannon")
kable(head(tab2))
ps1.meta2 <- meta(ad2)
kable(head(ps1.meta))
ps1.meta2$Shannon <- tab2$diversity_shannon 
# create a list of pairwise comaprisons
fam2 <- unique(ps1.meta2$resitance_14_21) # get the variables
# make a pairwise list that we want to compare.
fam.pairs2 <- combn(seq_along(fam2), 2, simplify = FALSE, FUN = function(i)fam2[i])
print(fam.pairs2)
#ps1.meta$'' <- alpha(ps1, index = 'shannon')
p2 <- ggboxplot(ps1.meta2, x = "resitance_14_21", y = "Shannon",
 add = "boxplot", fill = "resitance_14_21", order = c("Hyper Sensitive", "Sensitive", "Tolerant","Resistant", "Super Resistant")) + theme_classic() + theme(axis.text.x = element_text(angle = 45, hjust =1)) + scale_fill_viridis_d() + 
  labs(fill='Thermal Tolerance', title="Shannon-Wiener Alpha Diversity of Prokaryome", x="Thermal Tolerance", y="Shannon-Wiener Diversity Index") + ylim(0,8)
p2 <- p2 + stat_compare_means(comparisons = fam.pairs2) 
print(p2)

p3 <- ggarrange(p2, p1, nrow=2, align="v", legend="none")

p3


pdf("Fig3S_Alpha_res.pdf", width=4, height=8)
plot(p3)
dev.off()
```

```{r}
ps_clr_euk <- microbiome::transform(noport, 'clr', shift = 1)
psr_clr.ord_euk <- ordinate(ps_clr_euk, "RDA", "euclidean")
PCA_euk = plot_ordination(ps_clr_euk, psr_clr.ord_euk, 
                                color="region",
                                title="Aitchison Distance PCA of Eukaryome") + theme_classic() + geom_point(aes(color = region), alpha = 0.8, size = 3) + scale_colour_viridis_d() + labs(color="Region") + stat_ellipse()

PCA_euk


ps_clr_bac <- microbiome::transform(noport_bac, 'clr', shift = 1)
psr_clr.ord_bac <- ordinate(ps_clr_bac, "RDA", "euclidean")
PCA_bac = plot_ordination(ps_clr_bac, psr_clr.ord_bac, 
                                color="region",
                                title="Aitchison Distance PCA of Prokaryome") + theme_classic() + geom_point(aes(color = region), alpha = 0.8, size = 3) + scale_colour_viridis_d() + labs(color="Region") + stat_ellipse()

PCA_bac

PCA <- ggarrange(PCA_bac,PCA_euk, nrow=2, align="v", common.legend = TRUE, legend="right")

PCA


pdf("Fig4S-Beta-region.pdf", width=8, height=8)
plot(PCA)
dev.off()
```

### Beta Stats
```{r}
library(ALDEx2);packageVersion("ALDEx2")
library(vegan); packageVersion("vegan")
library(CoDaSeq); packageVersion("CoDaSeq")

taxon <- noport_bac@tax_table
d.czm <- cmultRepl(noport_bac@otu_table, method="CZM", label=0)
d.clr <- codaSeq.clr(d.czm)
E.clr <- t(d.clr)
d.pcx <- prcomp(E.clr)
dist.clr <- dist(E.clr)

var1 <- noport_bac@sam_data$region 
ano.var1 <- anosim(dist.clr, var1, permutations=999)
plot(ano.var1)

perm<-adonis(dist.clr~region,as(sample_data(noport_bac),"data.frame"))
print(perm)

```

```{r}
taxon <- noport@tax_table
d.czm <- cmultRepl(noport@otu_table, method="CZM", label=0)
d.clr <- codaSeq.clr(d.czm)
E.clr <- t(d.clr)
d.pcx <- prcomp(E.clr)
dist.clr <- dist(E.clr)

var1 <- noport@sam_data$region 
ano.var1 <- anosim(dist.clr, var1, permutations=999)
plot(ano.var1)

perm<-adonis(dist.clr~region,as(sample_data(noport),"data.frame"))
print(perm)
```

```{r}
ps_clr_euk <- microbiome::transform(noport, 'clr', shift = 1)
psr_clr.ord_euk <- ordinate(ps_clr_euk, "RDA", "euclidean")
PCA_euk = plot_ordination(ps_clr_euk, psr_clr.ord_euk, 
                                color="resitance_14_21",
                                title="Aitchison Distance PCA of Eukaryome") + theme_classic() + geom_point(aes(color = resitance_14_21), alpha = 0.8, size = 3) + scale_colour_viridis_d() + labs(color="Thermal Tolerance") + stat_ellipse()

PCA_euk


ps_clr_bac <- microbiome::transform(noport_bac, 'clr', shift = 1)
psr_clr.ord_bac <- ordinate(ps_clr_bac, "RDA", "euclidean")
PCA_bac = plot_ordination(ps_clr_bac, psr_clr.ord_bac, 
                                color="resitance_14_21",
                                title="Aitchison Distance PCA of Prokaryome") + theme_classic() + geom_point(aes(color = resitance_14_21), alpha = 0.8, size = 3) + scale_colour_viridis_d() + labs(color="Thermal Tolerance") + stat_ellipse()

PCA_bac

PCA <- ggarrange(PCA_bac,PCA_euk, nrow=2, align="v", common.legend = TRUE, legend="right")

PCA


pdf("Fig4S-Beta-Res.pdf", width=8, height=8)
plot(PCA)
dev.off()
```

```{r}
taxon <- noport@tax_table
d.czm <- cmultRepl(noport@otu_table, method="CZM", label=0)
d.clr <- codaSeq.clr(d.czm)
E.clr <- t(d.clr)
d.pcx <- prcomp(E.clr)
dist.clr <- dist(E.clr)

var1 <- noport@sam_data$resitance_14_21 
ano.var1 <- anosim(dist.clr, var1, permutations=999)
plot(ano.var1)

perm<-adonis(dist.clr~resitance_14_21,as(sample_data(noport),"data.frame"))
print(perm)
```
```{r}
taxon <- noport_bac@tax_table
d.czm <- cmultRepl(noport_bac@otu_table, method="CZM", label=0)
d.clr <- codaSeq.clr(d.czm)
E.clr <- t(d.clr)
d.pcx <- prcomp(E.clr)
dist.clr <- dist(E.clr)

var1 <- noport_bac@sam_data$resitance_14_21 
ano.var1 <- anosim(dist.clr, var1, permutations=999)
plot(ano.var1)

perm<-adonis(dist.clr~resitance_14_21,as(sample_data(noport_bac),"data.frame"))
print(perm)
```

## Figure 5S. Bubble Plot of Prok Thermal Tolerances (Endozoicomonas Removed)
```{r}
no_endo <- subset_taxa(noport_bac, (Family!="Endozoicomonadaceae"| is.na(Family)))
bub <- merge_samples(no_endo, "resitance_14_21") 
type_taxa <- bub %>% 
  tax_glom(taxrank = "Order") %>% 
  transform_sample_counts(function(x) {x/sum(x)*100} )  

type_taxa <- type_taxa %>% 
  psmelt() %>% 
  arrange(Abundance) 


library(data.table)
# create dataframe from phyloseq object
dat <- data.table(type_taxa)
# convert Phylum to a character vector from a factor because R
dat$Order <- as.character(dat$Order)
# group dataframe by Phylum, calculate median rel. abundance
dat[, median := median(Abundance, na.rm = FALSE), 
    by = "Order"]
# Change name to remainder of Phylum less than 2%
dat[(median <= 0.01), Order := "Below Threshold"]
dat[(Order == "Below Threshold"), Phylum := "Other"]

dat$Order[dat$Order == "Omnitrophia_NA"] <- "Omnitrophia IS"
dat$Order[dat$Order == "Gammaproteobacteria_NA"] <- "Gammaproteobacteria IS"
dat$Order[dat$Order == "Bacilli_NA"] <- "Bacilli IS"
dat$Order[dat$Order == "Bacteria_NA"] <- "Bacteria IS"
dat$Order[dat$Order == "Bacillariophyta_X"] <- "Bacillariophyta IS"
dat$Phylum[dat$Phylum == "Bacteria_NA"] <- "Bacteria IS"
dat$Order[dat$Order == "Alphaproteobacteria_NA"] <- "Alphaproteobacteria IS"

my_title <- expression(paste("Prokaryotic Orders within ", italic("P. clavata")))

xx <- ggplot(dat[Abundance > 0], aes(x = factor(Sample, levels=c("Hyper Sensitive", "Sensitive", "Tolerant","Resistant", "Super Resistant")), y = factor(Order, levels=bac_orders))) + geom_point(aes(size = Abundance, fill=Phylum), alpha = 1, shape = 21) + 
  scale_size_continuous(limits = c(0.000001, 100), range = c(0.1,10), breaks = c(1,10,50,75)) + 
  labs( x= "Thermal Tolerance", y = "Prokaryotic Order", size = "Relative Abundance %", fill="Prokaryotic Phylum") + theme_bw() +  
  scale_fill_manual(values = c25, breaks=c('Verrucomicrobiota', 'Proteobacteria', 'Firmicutes', 'Cyanobacteria', 'Bacteroidota', 'Campilobacterota', 'Bacteria IS', 'Other')) + theme(axis.text.x = element_text(angle = 40, hjust = 1)) + 
  ggtitle(label=my_title, subtitle = "With no Endozoicomonadaceae \n& a median relative abundance above 1%") 
xx

pdf("Fig5S-BacRes_noEndo.pdf", width=7, height=5)
plot(xx)
dev.off()
```


## Figure 6S. Dinoflagellate Tree (Populations)
Extract Dino ASVs
```{r}
mergedGP <- subset_taxa(psf_euk_coral_Tmin, Division=="Dinoflagellata")
f1<- filterfun_sample(topf(0.50)) # keep DINO ASV reads only if they are in the most abundant 50% of Dinos in at least 1 of the samples in dataset
wh1 <- genefilter_sample(mergedGP, f1, A=2)
mergedGP2 <- prune_taxa(wh1, mergedGP)
df <- data.frame(mergedGP2@tax_table)

write.csv(rownames(df), "/Volumes/projects/bonacolta/pcla/paramuricea_eukaryome/new/analysis/trees/Dino_ASVs.csv")
# Correct Sheet so that only ASVs are listed
"/Volumes/projects/bonacolta/pcla/paramuricea_eukaryome/new/analysis/trees/Dino/Dino_ASVs.txt"
```
```{bash}
cd /Volumes/projects/bonacolta/pcla/paramuricea_eukaryome/new/analysis/trees/Dino/

grep -w -A 1 -f  Dino_ASVs.txt ASVs.fa | grep -v -- "^--$" > pcla_Dinos_ASVs.fa

mafft --auto pcla_Dinos_ASVs.fa > pcla_Dinos_ASVs.aligned.fa

raxmlHPC-PTHREADS -T 4 -m GTRCAT -p 31415 -x 20398 -d -f a -N 1000 -n pcla_Dinos_ASVs -s pcla_Dinos_ASVs.aligned.fa 

sed 's/QUERY___//g' pcla_Dinos_ASVs | sed 's/\[I[0-9]*\]//g' > pcla_Dinos_ASVs.tre
```
```{bash}
cat /Volumes/projects/bonacolta/pcla/paramuricea_eukaryome/new/analysis/ASVs_taxonomy-curated-FINAL_2.txt | grep -w -A 1 -f Dino_ASVs.txt > pcla_Dino_ASVs_names.txt 

# Take out bad info a relabel for tree
```

```{r}
mergedGP <- noport %>% merge_samples("population")
ASVs <- read.delim("/Volumes/projects/bonacolta/pcla/paramuricea_eukaryome/new/analysis/trees/Dino/Dino_ASVs.txt", header=FALSE)
ASVs  <- ASVs  %>% pull(V1)
my_subset <- subset(t(mergedGP@otu_table@.Data), rownames(t(mergedGP@otu_table@.Data)) %in% ASVs)
my_subset1 <- phyloseq(otu_table(my_subset, taxa_are_rows=TRUE))
mergedGP <- merge_phyloseq(my_subset1, mergedGP@tax_table, mergedGP@sam_data)
mergedGP <- mergedGP %>%  transform_sample_counts(function(x) {x/sum(x)*100} )
tr <- read.tree("/Volumes/projects/bonacolta/pcla/paramuricea_eukaryome/new/analysis/trees/Dino/pcla_Dinos_ASVs.tre")
#Made TXT with annotated names plus all the ASVS
new_tips <- read.delim("/Volumes/projects/bonacolta/pcla/paramuricea_eukaryome/new/analysis/trees/Dino/pcla_Dino_ASVs_names.txt", header = TRUE)
tr <- sub.taxa.label(tr, new_tips)
#tr <- drop.tip(tr, c("KT806396_Outgroup", "KT806398_Outgroup", "GU825688_Outgroup"), trim.internal = TRUE)
tr<- root(tr, node =37)

spec <- tax_table(mergedGP) %>% data.frame(stringsAsFactors = FALSE) %>% tibble::rownames_to_column("otu")
p <- ggtree(tr, branch.length = "y", scale=0.09) %<+% spec 

#flip node 74
p <- flip(p, 40, 37)
#p +geom_text(aes(label=node))
gd <- p$data
melt_data<- psmelt(mergedGP)

melt_data[] <- lapply(melt_data, function(x) {
   inds <- match(x, new_tips$tip)
   ifelse(is.na(inds),x, new_tips$new_name[inds]) 
})

tt <- melt_data %>% left_join(select(gd,OTU=label,x,y),by="OTU") %>%
  arrange(factor(Sample, levels=ordered)) %>%  mutate(sample2=factor(Sample,levels=unique(Sample)),
  col=as.numeric(sample2),x.col=scales::rescale(col,to=c(0.80,1.15)))
#g <- p + geom_tiplab(size = 2, align=TRUE, linesize=.25)  + geom_treescale(x=0.05, y=0, offset=0.2, fontsize = 2.5)  +
#  geom_tile(data=tt,aes(x=x.col,y=y,fill=factor(Sample, levels = coral_order),alpha=Abundance)) + 
#  theme(legend.position="right", plot.title = element_text(size = 15, face = "bold", hjust = 0.5), legend.title=element_text(size=10, face="bold"), legend.text=element_text(size=8))  + ggtitle("Apicomplexa ASVs between Cnidarian Families") +
#  scale_alpha_continuous(limits=c(0.001,100),na.value=0, range = c(0.25, 1)) + scale_fill_manual(values=c25) +scale_colour_viridis_d(option="magma") +
#  labs(fill="Cnidarian Family", alpha= "Relative Abundance") +
#  theme(panel.grid.major.y=element_line(), panel.grid.minor.y=element_line())
#g


##Changing heatmap
g <- p + geom_tiplab(size = 4, align=TRUE, linesize=.20, hjust="right", offset=0.40, linetype=NA)  + geom_treescale(x=0.05, y=-0.5, offset=0.2, fontsize = 2.5)  +
  geom_tile(data=tt,aes(x=x.col,y=y,fill=Abundance)) + 
  theme(legend.position="right", plot.title = element_text(size = 15, face = "bold", hjust = 0.5), legend.title=element_text(size=10, face="bold"), legend.text=element_text(size=8)) +
  labs(fill="Relative Abundance") + scale_fill_gradient2(low="transparent", high = "#3182bd", mid= "#deebf7",midpoint= 5,limits=c(0.0001, 100), na.value="transparent") +
  scale_y_continuous(minor_breaks = seq(1 , 52, 1), breaks = seq(1, 52, 1), expand = c(0.013, 1)) +  scale_x_continuous(minor_breaks = seq(0.80,1.15, 0.035), breaks = seq(0.80,1.15, 0.035)) +
  theme(panel.grid.major.x=element_line(size = (0.2), colour="lightgrey"), panel.grid.minor.x=element_line(size = (0.2), colour="grey"), axis.title.y = element_blank())
g
g$data
## Combine again at OTU the use this reads plot.
#Bar Plot
mergedGP2 <- noport %>% merge_samples("time")

my_subsett <- subset(t(mergedGP2@otu_table@.Data), rownames(t(mergedGP2@otu_table@.Data)) %in% ASVs)
my_subsett1 <- phyloseq(otu_table(my_subsett, taxa_are_rows=TRUE))
mergedGP2 <- merge_phyloseq(my_subsett1, mergedGP2@tax_table, mergedGP2@sam_data)

glom <- mergedGP2  %>%  transform_sample_counts(function(x) {x/sum(x)*100} )
glom # should list # taxa as # phyla
data <- psmelt(glom) 

data[] <- lapply(data, function(x) {
   inds <- match(x, new_tips$tip)
   ifelse(is.na(inds),x, new_tips$new_name[inds]) 
})


# create dataframe from phyloseq object
#data$Order <- as.character(data$Order) #convert to character
ttt <- g$data
ttt <- ttt[with(ttt, order(+y)), ]
target <- as.vector(ttt$label)
tttt <- ttt[!duplicated(ttt["label"]), ]
names(tttt)[names(tttt) == "label"] <- "OTU"
data2 <- merge(data, tttt, by='OTU')
data3 <- data2[data2$Abundance != "NaN", ] 
# Add Accession names to Data3
as <- ttt[!grepl("0.", ttt$label),]
as <- as[!is.na(as$label), ]
ass <- as.vector(as$label)
data4 <- data3
library(gdata)

data4 <- data4[order(match(data4$OTU, target)), , drop = FALSE]
# Add Sample count per OTU
mergedGP2
## This object has all the info. I want to extract OTU Table. Then Count how many columns have a number greater than 0. I will export thi snumber and graph it.
df <- noport@otu_table@.Data
df <- data.frame(df)
df$sample_count <- apply(df[, grep("", names(df))], MARGIN = 1, 
                function(x) sum(x > 0, na.rm = T))
df$sample_total <- apply(df[, grep("", names(df))], MARGIN = 1, 
                function(x) sum(x >= 0, na.rm = T))
df$sample_percent <- df$sample_count / df$sample_total *100


row.names(df) <- lapply(row.names(df), function(x) {
   inds <- match(x, new_tips$tip)
   ifelse(is.na(inds),x, new_tips$new_name[inds]) 
})

df2 <- subset(df, row.names(df) %in% target)


df2 <- df2[order(match(rownames(df2), target)), , drop = FALSE]

#Match Samples then add zeroes for not listed
samples <- as.vector(df2$sample_percent)
data4$sample_percent=samples
library(reshape2)

b <- ggplot(data=data4, aes(x=y, y=Abundance, na.rm = TRUE)) + theme_classic() + geom_bar(stat="identity", fill = "#55C667FF") + coord_flip() +
      theme(axis.title.y = element_blank(), axis.text.y = element_blank(), axis.text.x= element_text(size=4), axis.title.x= element_text(size=9)) + scale_y_continuous(expand = c(0, 0), na.value=0, position = "right", breaks=c(0, 15, 30)) + guides(fill=guide_legend(title="Value")) + ylab("Abundance %") +
  scale_x_continuous(expand = c(0.00, 0), na.value=0, limits=c(-1.5, 28.5))

b
c <- ggplot(data=data4, aes(x=y, y=sample_percent, na.rm = TRUE)) + theme_classic() + geom_bar(stat="identity", fill = "#482677FF") + coord_flip() +
      theme(axis.title.y = element_blank(), axis.text.y = element_blank(), axis.text.x= element_text(size=4), axis.title.x= element_text(size=9)) + scale_y_continuous(expand = c(0, 0), na.value=0, position = "right", breaks=c(0,25,50, 75)) + guides(fill=guide_legend(title="Value")) + ylab("Sample %") +
  scale_x_continuous(expand = c(0.00, 0), na.value=0, limits=c(-1.5, 28.5))
c

a<- ggarrange(b, c, ncol=2, nrow=1, align = "h", common.legend = TRUE, legend="right") 

z <- ggarrange(g, a, ncol=2, nrow=1, widths = c(0.85,.25), align = "v", common.legend = TRUE, legend="right") 
z

zz <- annotate_figure(z, fig.lab = "Heatmap of Dinoflagellate ASVs across Sampling Locations", fig.lab.face = "bold", fig.lab.size = 14, fig.lab.pos = "top.left")

pdf("Fig6S-SynTree.pdf", width=14, height=6)
plot(zz)
dev.off()
```
## Figure 7S. Ciliate Tree (Populations)
Extract ASVs (kept top 31). Need to build reference tree too!
```{r}
mergedGP <- subset_taxa(psf_euk_coral_Tmin, Division=="Ciliophora")
#f1<- filterfun_sample(topf(0.50)) # keep ASV reads only if they are in the most abundant 50% of Dinos in at least 1 of the samples in dataset
#wh1 <- genefilter_sample(mergedGP, f1, A=2)
#mergedGP2 <- prune_taxa(wh1, mergedGP)
df <- data.frame(mergedGP@tax_table)

write.csv(rownames(df), "/Volumes/projects/bonacolta/pcla/paramuricea_eukaryome/new/analysis/trees/Ciliates/Ciliates_ASVs.csv")
# Correct Sheet so that only ASVs are listed
"/Volumes/projects/bonacolta/pcla/paramuricea_eukaryome/new/analysis/trees/Ciliates/Ciliates_ASVs.txt"
```
```{r}
mergedGP <- subset_taxa(psf_euk_coral_Tmin, Division=="Dinoflagellata")
f1<- filterfun_sample(topf(0.50)) # keep DINO ASV reads only if they are in the most abundant 50% of Dinos in at least 1 of the samples in dataset
wh1 <- genefilter_sample(mergedGP, f1, A=2)
mergedGP2 <- prune_taxa(wh1, mergedGP)
df <- data.frame(mergedGP2@tax_table)

write.csv(rownames(df), "/Volumes/projects/bonacolta/pcla/paramuricea_eukaryome/new/analysis/trees/Dino_ASVs.csv")
# Correct Sheet so that only ASVs are listed
"/Volumes/projects/bonacolta/pcla/paramuricea_eukaryome/new/analysis/trees/Dino/Dino_ASVs.txt"
```
```{bash}
cd /Volumes/projects/bonacolta/pcla/paramuricea_eukaryome/new/analysis/trees/Ciliates/

mafft --auto pcla_Ciliates_ASVs.fa > pcla_Ciliates_ASVs.aligned.fa

raxmlHPC-PTHREADS -T 4 -m GTRCAT -p 31415 -x 20398 -d -f a -N 1000 -n pcla_Ciliates_ASVs -s pcla_Ciliates_ASVs.aligned.fa

sed 's/QUERY___//g' RAxML_bestTree.pcla_Ciliates_ASVs | sed 's/\[I[0-9]*\]//g' > pcla_Ciliates_ASVs.tre
```
```{bash}
cat /Volumes/projects/bonacolta/pcla/paramuricea_eukaryome/new/analysis/ASVs_taxonomy-curated-FINAL_2.txt | grep -w -A 1 -f Ciliates_ASVs.txt |  grep -v -- "^--$" >  > pcla_Ciliates_ASVs_names.txt 

# Take out bad info a relabel for tree
```
```{r}
mergedGP <- noport %>% merge_samples("population")
ASVs <- read.delim("/Volumes/projects/bonacolta/pcla/paramuricea_eukaryome/new/analysis/trees/Ciliates/Ciliates_ASVs.txt", header=FALSE)
ASVs  <- ASVs  %>% pull(V1)
my_subset <- subset(t(mergedGP@otu_table@.Data), rownames(t(mergedGP@otu_table@.Data)) %in% ASVs)
my_subset1 <- phyloseq(otu_table(my_subset, taxa_are_rows=TRUE))
mergedGP <- merge_phyloseq(my_subset1, mergedGP@tax_table, mergedGP@sam_data)
mergedGP <- mergedGP %>%  transform_sample_counts(function(x) {x/sum(x)*100} )
tr <- read.tree("/Volumes/projects/bonacolta/pcla/paramuricea_eukaryome/new/analysis/trees/Ciliates/pcla_Ciliates_ASVs.tre")
#Made TXT with annotated names plus all the ASVS
new_tips <- read.delim("/Volumes/projects/bonacolta/pcla/paramuricea_eukaryome/new/analysis/trees/Ciliates/pcla_Ciliates_ASVs_names.txt", header = TRUE)
tr <- sub.taxa.label(tr, new_tips)
tr<- root(tr, outgroup ="ASV_126_Endogenida_2_X_sp.")
tr <- drop.tip(tr, "ASV_126_Endogenida_2_X_sp.", trim.internal = TRUE)

spec <- tax_table(mergedGP) %>% data.frame(stringsAsFactors = FALSE) %>% tibble::rownames_to_column("otu")
p <- ggtree(tr, branch.length = "y", scale=0.09) %<+% spec 

#p +geom_text(aes(label=node))
#flip node 74
#p <- flip(p, 40, 37)

gd <- p$data
melt_data<- psmelt(mergedGP)

melt_data[] <- lapply(melt_data, function(x) {
   inds <- match(x, new_tips$tip)
   ifelse(is.na(inds),x, new_tips$new_name[inds]) 
})

tt <- melt_data %>% left_join(select(gd,OTU=label,x,y),by="OTU") %>%
  arrange(factor(Sample, levels=ordered)) %>%  mutate(sample2=factor(Sample,levels=unique(Sample)),
  col=as.numeric(sample2),x.col=scales::rescale(col,to=c(1.60,2.2)))
#g <- p + geom_tiplab(size = 2, align=TRUE, linesize=.25)  + geom_treescale(x=0.05, y=0, offset=0.2, fontsize = 2.5)  +
#  geom_tile(data=tt,aes(x=x.col,y=y,fill=factor(Sample, levels = coral_order),alpha=Abundance)) + 
#  theme(legend.position="right", plot.title = element_text(size = 15, face = "bold", hjust = 0.5), legend.title=element_text(size=10, face="bold"), legend.text=element_text(size=8))  + ggtitle("Apicomplexa ASVs between Cnidarian Families") +
#  scale_alpha_continuous(limits=c(0.001,100),na.value=0, range = c(0.25, 1)) + scale_fill_manual(values=c25) +scale_colour_viridis_d(option="magma") +
#  labs(fill="Cnidarian Family", alpha= "Relative Abundance") +
#  theme(panel.grid.major.y=element_line(), panel.grid.minor.y=element_line())
#g


##Changing heatmap
g <- p + geom_tiplab(size = 4, align=TRUE, linesize=.20, hjust="right", offset=0.58, linetype=NA)  + geom_treescale(x=0.05, y=0, offset=0.2, fontsize = 2.5)  +
  geom_tile(data=tt,aes(x=x.col,y=y,fill=Abundance)) + 
  theme(legend.position="right", plot.title = element_text(size = 15, face = "bold", hjust = 0.5), legend.title=element_text(size=10, face="bold"), legend.text=element_text(size=8)) +
  labs(fill="Relative Abundance") + scale_fill_gradient2(low="transparent", high = "#3182bd", mid= "#deebf7",midpoint= 5,limits=c(0.0001, 100), na.value="transparent") +
  scale_y_continuous(minor_breaks = seq(1 , 52, 1), breaks = seq(1, 52, 1), expand = c(0, 0.8)) +  scale_x_continuous(minor_breaks = seq(1.6,2.2, 0.06), breaks = seq(1.6,2.2, 0.06)) +
  theme(panel.grid.major.x=element_line(size = (0.2), colour="lightgrey"), panel.grid.minor.x=element_line(size = (0.2), colour="grey"), axis.title.y = element_blank())
g
g$data
## Combine again at OTU the use this reads plot.
#Bar Plot
mergedGP2 <- noport %>% merge_samples("time")

my_subsett <- subset(t(mergedGP2@otu_table@.Data), rownames(t(mergedGP2@otu_table@.Data)) %in% ASVs)
my_subsett1 <- phyloseq(otu_table(my_subsett, taxa_are_rows=TRUE))
mergedGP2 <- merge_phyloseq(my_subsett1, mergedGP2@tax_table, mergedGP2@sam_data)

glom <- mergedGP2  %>%  transform_sample_counts(function(x) {x/sum(x)*100} )
glom # should list # taxa as # phyla
data <- psmelt(glom) 

data[] <- lapply(data, function(x) {
   inds <- match(x, new_tips$tip)
   ifelse(is.na(inds),x, new_tips$new_name[inds]) 
})


# create dataframe from phyloseq object
#data$Order <- as.character(data$Order) #convert to character
ttt <- g$data
ttt <- ttt[with(ttt, order(+y)), ]
target <- as.vector(ttt$label)
tttt <- ttt[!duplicated(ttt["label"]), ]
names(tttt)[names(tttt) == "label"] <- "OTU"
data2 <- merge(data, tttt, by='OTU')
data3 <- data2[data2$Abundance != "NaN", ] 
# Add Accession names to Data3
as <- ttt[!grepl("0.", ttt$label),]
as <- as[!is.na(as$label), ]
ass <- as.vector(as$label)
data4 <- data3
library(gdata)

data4 <- data4[order(match(data4$OTU, target)), , drop = FALSE]
# Add Sample count per OTU
mergedGP2
## This object has all the info. I want to extract OTU Table. Then Count how many columns have a number greater than 0. I will export thi snumber and graph it.
df <- noport@otu_table@.Data
df <- data.frame(df)
df$sample_count <- apply(df[, grep("", names(df))], MARGIN = 1, 
                function(x) sum(x > 0, na.rm = T))
df$sample_total <- apply(df[, grep("", names(df))], MARGIN = 1, 
                function(x) sum(x >= 0, na.rm = T))
df$sample_percent <- df$sample_count / df$sample_total *100


row.names(df) <- lapply(row.names(df), function(x) {
   inds <- match(x, new_tips$tip)
   ifelse(is.na(inds),x, new_tips$new_name[inds]) 
})

df2 <- subset(df, row.names(df) %in% target)


df2 <- df2[order(match(rownames(df2), target)), , drop = FALSE]

#Match Samples then add zeroes for not listed
samples <- as.vector(df2$sample_percent)
data4$sample_percent=samples
library(reshape2)

b <- ggplot(data=data4, aes(x=y, y=Abundance, na.rm = TRUE)) + theme_classic() + geom_bar(stat="identity", fill = "#55C667FF") + coord_flip() +
      theme(axis.title.y = element_blank(), axis.text.y = element_blank(), axis.text.x= element_text(size=4), axis.title.x= element_text(size=9)) + scale_y_continuous(expand = c(0, 0), na.value=0, position = "right", breaks=c(0, 25, 50)) + guides(fill=guide_legend(title="Value")) + ylab("Abundance %") +
  scale_x_continuous(expand = c(0.00, 0), na.value=0, limits=c(-1, 21.5))

b
c <- ggplot(data=data4, aes(x=y, y=sample_percent, na.rm = TRUE)) + theme_classic() + geom_bar(stat="identity", fill = "#482677FF") + coord_flip() +
      theme(axis.title.y = element_blank(), axis.text.y = element_blank(), axis.text.x= element_text(size=4), axis.title.x= element_text(size=9)) + scale_y_continuous(expand = c(0, 0), na.value=0, position = "right", breaks=c(0,25, 50, 75)) + guides(fill=guide_legend(title="Value")) + ylab("Sample %") +
  scale_x_continuous(expand = c(0.00, 0), na.value=0, limits=c(-1, 21.5))
c

a<- ggarrange(b, c, ncol=2, nrow=1, align = "h", common.legend = TRUE, legend="right") 

z <- ggarrange(g, a, ncol=2, nrow=1, widths = c(1.1,.25), align = "v", common.legend = TRUE, legend="right") 
z

zz <- annotate_figure(z, fig.lab = "Heatmap of Ciliate ASVs across Sampling Locations", fig.lab.face = "bold", fig.lab.size = 14, fig.lab.pos = "top.left")


pdf("Fig7S-CilTree.pdf", width=14, height=6)
plot(zz)
dev.off()
```




## Figure 8S. Big tree of Microeukaroytic Clade Thermotolerances
```{r}
noport <- subset_samples(psf_euk_coral_Tmin, psf_euk_coral_Tmin@sam_data$region!="Portugal")
mergedGP <- noport %>% merge_samples("resitance_14_21")
ASVs <- read.delim("/Volumes/projects/bonacolta/pcla/paramuricea_eukaryome/new/analysis/trees/combined_asvs.txt", header=FALSE)
ASVs  <- ASVs  %>% pull(V1)
my_subset <- subset(t(mergedGP@otu_table@.Data), rownames(t(mergedGP@otu_table@.Data)) %in% ASVs)
my_subset1 <- phyloseq(otu_table(my_subset, taxa_are_rows=TRUE))
mergedGP <- merge_phyloseq(my_subset1, mergedGP@tax_table, mergedGP@sam_data)
mergedGP <- mergedGP %>%  transform_sample_counts(function(x) {x/sum(x)*100} )
tr <- read.tree("/Volumes/projects/bonacolta/pcla/paramuricea_eukaryome/new/analysis/trees/Ciliates/pcla_Ciliates_ASVs.tre")
#Made TXT with annotated names plus all the ASVS
new_tips <- read.delim("/Volumes/projects/bonacolta/pcla/paramuricea_eukaryome/new/analysis/trees/Ciliates/pcla_Ciliates_ASVs_names.txt", header = TRUE)
tr <- sub.taxa.label(tr, new_tips)
tr<- root(tr, outgroup ="ASV_126_Endogenida_2_X_sp.")
tr <- drop.tip(tr, "ASV_126_Endogenida_2_X_sp.", trim.internal = TRUE)

spec <- tax_table(mergedGP) %>% data.frame(stringsAsFactors = FALSE) %>% tibble::rownames_to_column("otu")
p <- ggtree(tr, branch.length = "y", scale=0.09) %<+% spec 

gd <- p$data
melt_data<- psmelt(mergedGP)
ordered<- c("Hypersensible", "Sensible", "Tolerant","Resistant", "Superresistant")


melt_data[] <- lapply(melt_data, function(x) {
   inds <- match(x, new_tips$tip)
   ifelse(is.na(inds),x, new_tips$new_name[inds]) 
})

tt <- melt_data %>% left_join(select(gd,OTU=label,x,y),by="OTU") %>%
  arrange(factor(Sample, levels=ordered)) %>%  mutate(sample2=factor(Sample,levels=unique(Sample)),
  col=as.numeric(sample2),x.col=scales::rescale(col,to=c(1.60,2.2)))

cil <- p + geom_tiplab(size = 2, align=TRUE, linesize=.20, hjust="right", offset=0.50, linetype=NA)  + geom_treescale(x=0.05, y=0, offset=0.2, fontsize = 2.5)  +
  geom_tile(data=tt,aes(x=x.col,y=y,fill=Abundance)) + 
  theme(legend.position="right", plot.title = element_text(size = 15, face = "bold", hjust = 0.5), legend.title=element_text(size=10, face="bold"), legend.text=element_text(size=8)) +
  labs(fill="Relative Abundance") + scale_fill_gradient2(low="transparent", high = "#3182bd", mid= "#deebf7",midpoint= .5,limits=c(0.0001, 100), na.value="transparent") +
  scale_y_continuous(minor_breaks = seq(1 , 52, 1), breaks = seq(1, 52, 1), expand = c(0.013, 1)) +  scale_x_continuous(minor_breaks = seq(1.6,2.2, 0.15), breaks = seq(1.6,2.2, 0.15)) +
  theme(panel.grid.major.x=element_line(size = (0.2), colour="lightgrey"), panel.grid.minor.x=element_line(size = (0.2), colour="grey"), axis.title.y = element_blank())
cil
noport <- subset_samples(psf_euk_coral_Tmin, psf_euk_coral_Tmin@sam_data$region!="Portugal")
mergedGP <- noport %>% merge_samples("resitance_14_21")
ASVs <- read.delim("/Volumes/projects/bonacolta/pcla/paramuricea_eukaryome/new/analysis/trees/combined_asvs.txt", header=FALSE)
ASVs  <- ASVs  %>% pull(V1)
my_subset <- subset(t(mergedGP@otu_table@.Data), rownames(t(mergedGP@otu_table@.Data)) %in% ASVs)
my_subset1 <- phyloseq(otu_table(my_subset, taxa_are_rows=TRUE))
mergedGP <- merge_phyloseq(my_subset1, mergedGP@tax_table, mergedGP@sam_data)
mergedGP <- mergedGP %>%  transform_sample_counts(function(x) {x/sum(x)*100} )
tr <- read.tree("/Volumes/projects/bonacolta/pcla/paramuricea_eukaryome/new/analysis/trees/Dino/pcla_Dinos_ASVs.tre")
#Made TXT with annotated names plus all the ASVS
new_tips <- read.delim("/Volumes/projects/bonacolta/pcla/paramuricea_eukaryome/new/analysis/trees/Dino/pcla_Dino_ASVs_names.txt", header = TRUE)
tr <- sub.taxa.label(tr, new_tips)
#tr <- drop.tip(tr, c("KT806396_Outgroup", "KT806398_Outgroup", "GU825688_Outgroup"), trim.internal = TRUE)
tr<- root(tr, node =37)

spec <- tax_table(mergedGP) %>% data.frame(stringsAsFactors = FALSE) %>% tibble::rownames_to_column("otu")
p <- ggtree(tr, branch.length = "y", scale=0.09) %<+% spec 

#flip node 74
p <- flip(p, 40, 37)
#p +geom_text(aes(label=node))
gd <- p$data
melt_data<- psmelt(mergedGP)

melt_data[] <- lapply(melt_data, function(x) {
   inds <- match(x, new_tips$tip)
   ifelse(is.na(inds),x, new_tips$new_name[inds]) 
})

tt <- melt_data %>% left_join(select(gd,OTU=label,x,y),by="OTU") %>%
  arrange(factor(Sample, levels=ordered)) %>%  mutate(sample2=factor(Sample,levels=unique(Sample)),
  col=as.numeric(sample2),x.col=scales::rescale(col,to=c(1.6,2.2)))

otdinos <- p + geom_tiplab(size = 2, align=TRUE, linesize=.20, hjust="right", offset=1.10, linetype=NA)  + geom_treescale(x=0.05, y=0, offset=0.2, fontsize = 2.5)  +
  geom_tile(data=tt,aes(x=x.col,y=y,fill=Abundance)) + 
  theme(legend.position="right", plot.title = element_text(size = 15, face = "bold", hjust = 0.5), legend.title=element_text(size=10, face="bold"), legend.text=element_text(size=8)) +
  labs(fill="Relative Abundance") + scale_fill_gradient2(low="transparent", high = "#3182bd", mid= "#deebf7",midpoint= .5,limits=c(0.0001, 100), na.value="transparent") +
  scale_y_continuous(minor_breaks = seq(1 , 52, 1), breaks = seq(1, 52, 1), expand = c(0.013, 1)) +  scale_x_continuous(minor_breaks = seq(1.6,2.2, 0.15), breaks = seq(1.6,2.2, 0.15)) +
  theme(panel.grid.major.x=element_line(size = (0.2), colour="lightgrey"), panel.grid.minor.x=element_line(size = (0.2), colour="grey"), axis.title.y = element_blank())
otdinos

noport <- subset_samples(psf_euk_coral_Tmin, psf_euk_coral_Tmin@sam_data$region!="Portugal")
mergedGP <- noport %>% merge_samples("resitance_14_21")
ASVs <- read.delim("/Volumes/projects/bonacolta/pcla/paramuricea_eukaryome/new/analysis/trees/combined_asvs.txt", header=FALSE)
ASVs  <- ASVs  %>% pull(V1)
my_subset <- subset(t(mergedGP@otu_table@.Data), rownames(t(mergedGP@otu_table@.Data)) %in% ASVs)
my_subset1 <- phyloseq(otu_table(my_subset, taxa_are_rows=TRUE))
mergedGP <- merge_phyloseq(my_subset1, mergedGP@tax_table, mergedGP@sam_data)
mergedGP <- mergedGP %>%  transform_sample_counts(function(x) {x/sum(x)*100} )
tr <- read.tree("/Volumes/projects/bonacolta/pcla/paramuricea_eukaryome/new/analysis/trees/Api/RAxML_placement_tree_pcla_Api.tre")
#Made TXT with annotated names plus all the ASVS
new_tips <- read.delim("/Volumes/projects/bonacolta/pcla/paramuricea_eukaryome/new/analysis/trees/Api/tree_anno.txt", header = TRUE)
tr <- sub.taxa.label(tr, new_tips)
tr <- drop.tip(tr, c("KT806396_Outgroup", "KT806398_Outgroup", "GU825688_Outgroup", NA), trim.internal = TRUE)
tr<- root(tr, outgroup ="KF579890_Corallicolidae_COR6_sp.")

spec <- tax_table(mergedGP) %>% data.frame(stringsAsFactors = FALSE) %>% tibble::rownames_to_column("otu")
p <- ggtree(tr, branch.length = "y", scale=0.09) %<+% spec 

#flip node 74
#p <- flip(p, 76, 75)

gd <- p$data
melt_data<- psmelt(mergedGP)
ordered<- c("Balun", "Mana","Altare","Indiano","Lighthouse","Gargallu","Palazzinu","Palazzu","La Vaca","Pota de Llop", "Tascons","Sagres")

tt <- melt_data %>% left_join(select(gd,OTU=label,x,y),by="OTU") %>%
  arrange(factor(Sample, levels=ordered)) %>%  mutate(sample2=factor(Sample,levels=unique(Sample)),
  col=as.numeric(sample2),x.col=scales::rescale(col,to=c(1.6,2.2)))

apires <- p + geom_tiplab(size = 2, align=TRUE, linesize=.20, hjust="right", offset=1.4, linetype=NA)  + geom_treescale(x=0.05, y=0, offset=0.2, fontsize = 2.5)  +
  geom_tile(data=tt,aes(x=x.col,y=y,fill=Abundance)) + 
  theme(legend.position="right", plot.title = element_text(size = 15, face = "bold", hjust = 0.5), legend.title=element_text(size=10, face="bold"), legend.text=element_text(size=8)) +
  labs(fill="Relative Abundance") + scale_fill_gradient2(low="transparent", high = "#3182bd", mid= "#deebf7",midpoint= .5,limits=c(0.0001, 100), na.value="transparent") +
  scale_y_continuous(minor_breaks = seq(1 , 52, 1), breaks = seq(1, 52, 1), expand = c(0.013, 1)) +  scale_x_continuous(minor_breaks = seq(1.6,2.2, 0.15), breaks = seq(1.6,2.2, 0.15)) +
  theme(panel.grid.major.x=element_line(size = (0.2), colour="lightgrey"), panel.grid.minor.x=element_line(size = (0.2), colour="grey"), axis.title.y = element_blank())
apires

glob <- ggarrange(cil, otdinos, apires, ncol=1, nrow=3, align="v", common.legend = TRUE, legend="right")
pdf("/Volumes/GoogleDrive/.shortcut-targets-by-id/1NZWDX6hj2iMLlcMpeA9ILkNyhxyngfoM/Bonacolta\ et\ al.\ 2020\ Paramuricea/manuscript/figures/Fig9S-TreeRes.pdf", width=8, height=10)
plot(glob)
dev.off()
```




##ANCOMS
### Now do a grid interactions for Proks and Euks 
### Fig10S: Grid of ANCOMBC-LFC for Prokaryotic Orders
```{r}
library(ANCOMBC)
library(DT)

noport_bac <- subset_samples(psf_bac_coral_Tmin, psf_bac_coral_Tmin@sam_data$region!="Portugal")

oldtax <- data.frame(tax_table(noport_bac))

oldtax$Order[oldtax$Order == "Gammaproteobacteria_NA"] <- "Gammaproteobacteria IS"
oldtax$Order[oldtax$Order == "Alphaproteobacteria_NA"] <- "Alphaproteobacteria IS"
oldtax$Order[oldtax$Order == "Bacilli_NA"] <- "Bacilli IS"
oldtax$Order[oldtax$Order == "Bacteria_NA"] <- "Bacteria IS"


tax_table(noport_bac) <- as.matrix(oldtax)
genus_data = aggregate_taxa(noport_bac, "Order")

out = ancombc(phyloseq = genus_data, formula = "resitance_14_21", 
              p_adj_method = "none", zero_cut = 0.90, lib_cut = 0, 
              group = "resitance_14_21", struc_zero = TRUE, neg_lb = TRUE, tol = 1e-5, 
              max_iter = 100, conserve = TRUE, alpha = 0.05, global = TRUE)

res = out$res
res_global = out$res_global

#HS_S
samp_frac = out$samp_frac
samp_frac[is.na(samp_frac)] = 0 
log_obs_abn = log(abundances(genus_data) + 1) 
log_obs_abn_adj = t(t(log_obs_abn) - samp_frac)
round(log_obs_abn_adj[, 1:6], 2) %>% 
  datatable(caption = "Bias-adjusted log observed abundances")
df_fig1 = data.frame(res$beta * res$diff_abn, check.names = FALSE) %>% 
  rownames_to_column("taxon_id")
df_fig2 = data.frame(res$se * res$diff_abn, check.names = FALSE) %>% 
  rownames_to_column("taxon_id")
colnames(df_fig2)[-1] = paste0(colnames(df_fig2)[-1], "SD")
df_fig = df_fig1 %>% left_join(df_fig2, by = "taxon_id") %>%
  transmute(taxon_id, resitance_14_21Sensitive, resitance_14_21SensitiveSD) %>% 
  filter(resitance_14_21Sensitive != 0) %>% arrange(desc(resitance_14_21Sensitive)) %>%
  mutate(group = ifelse(resitance_14_21Sensitive > 0, "g1", "g2"))
df_fig$taxon_id = factor(df_fig$taxon_id, levels = df_fig$taxon_id)
HS_S = ggplot(data = df_fig, 
           aes(x = taxon_id, y = resitance_14_21Sensitive, fill = resitance_14_21Sensitive, color = resitance_14_21Sensitive)) + 
  geom_bar(stat = "identity", width = 0.7, 
           position = position_dodge(width = 0.4)) + scale_fill_viridis_c(option = "plasma") + scale_color_viridis_c(option = "plasma") +
  geom_errorbar(aes(ymin = resitance_14_21Sensitive - resitance_14_21SensitiveSD, ymax = resitance_14_21Sensitive + resitance_14_21SensitiveSD), width = 0.2,
                position = position_dodge(0.05), color = "black") + 
  labs(x = "Prokaryotic Order", y = "Log fold change", 
       title = "Log Fold Change in ANCOM Significant Taxa: Hyper Sensitive vs Sensitive") + 
  theme_bw() + 
  theme(legend.position = "none",
        panel.grid.minor.y = element_blank()) + coord_flip() + scale_y_continuous(limits = c(-3, 3))
HS_S

#HS_T
samp_frac = out$samp_frac
samp_frac[is.na(samp_frac)] = 0 
log_obs_abn = log(abundances(genus_data) + 1) 
log_obs_abn_adj = t(t(log_obs_abn) - samp_frac)
round(log_obs_abn_adj[, 1:6], 2) %>% 
  datatable(caption = "Bias-adjusted log observed abundances")
df_fig1 = data.frame(res$beta * res$diff_abn, check.names = FALSE) %>% 
  rownames_to_column("taxon_id")
df_fig2 = data.frame(res$se * res$diff_abn, check.names = FALSE) %>% 
  rownames_to_column("taxon_id")
colnames(df_fig2)[-1] = paste0(colnames(df_fig2)[-1], "SD")
df_fig = df_fig1 %>% left_join(df_fig2, by = "taxon_id") %>%
  transmute(taxon_id, resitance_14_21Tolerant, resitance_14_21TolerantSD) %>% 
  filter(resitance_14_21Tolerant != 0) %>% arrange(desc(resitance_14_21Tolerant)) %>%
  mutate(group = ifelse(resitance_14_21Tolerant > 0, "g1", "g2"))
df_fig$taxon_id = factor(df_fig$taxon_id, levels = df_fig$taxon_id)
HS_T = ggplot(data = df_fig, 
           aes(x = taxon_id, y = resitance_14_21Tolerant, fill = resitance_14_21Tolerant, color = resitance_14_21Tolerant)) + 
  geom_bar(stat = "identity", width = 0.7, 
           position = position_dodge(width = 0.4)) + scale_fill_viridis_c(option = "plasma") + scale_color_viridis_c(option = "plasma") +
  geom_errorbar(aes(ymin = resitance_14_21Tolerant - resitance_14_21TolerantSD, ymax = resitance_14_21Tolerant + resitance_14_21TolerantSD), width = 0.2,
                position = position_dodge(0.05), color = "black") + 
  labs(x = "Prokaryotic Order", y = "Log fold change", 
       title = "Log Fold Change in ANCOM Significant Taxa: Hyper Sensitive vs Tolerant") + 
  theme_bw() + 
  theme(legend.position = "none",
        panel.grid.minor.y = element_blank()) + coord_flip() + scale_y_continuous(limits = c(-3, 3))
HS_T

#HS_R
samp_frac = out$samp_frac
samp_frac[is.na(samp_frac)] = 0 
log_obs_abn = log(abundances(genus_data) + 1) 
log_obs_abn_adj = t(t(log_obs_abn) - samp_frac)
round(log_obs_abn_adj[, 1:6], 2) %>% 
  datatable(caption = "Bias-adjusted log observed abundances")
df_fig1 = data.frame(res$beta * res$diff_abn, check.names = FALSE) %>% 
  rownames_to_column("taxon_id")
df_fig2 = data.frame(res$se * res$diff_abn, check.names = FALSE) %>% 
  rownames_to_column("taxon_id")
colnames(df_fig2)[-1] = paste0(colnames(df_fig2)[-1], "SD")
df_fig = df_fig1 %>% left_join(df_fig2, by = "taxon_id") %>%
  transmute(taxon_id, resitance_14_21Resistant, resitance_14_21ResistantSD) %>% 
  filter(resitance_14_21Resistant != 0) %>% arrange(desc(resitance_14_21Resistant)) %>%
  mutate(group = ifelse(resitance_14_21Resistant > 0, "g1", "g2"))
df_fig$taxon_id = factor(df_fig$taxon_id, levels = df_fig$taxon_id)
HS_R = ggplot(data = df_fig, 
           aes(x = taxon_id, y = resitance_14_21Resistant, fill = resitance_14_21Resistant, color = resitance_14_21Resistant)) + 
  geom_bar(stat = "identity", width = 0.7, 
           position = position_dodge(width = 0.4)) + scale_fill_viridis_c(option = "plasma") + scale_color_viridis_c(option = "plasma") +
  geom_errorbar(aes(ymin = resitance_14_21Resistant - resitance_14_21ResistantSD, ymax = resitance_14_21Resistant + resitance_14_21ResistantSD), width = 0.2,
                position = position_dodge(0.05), color = "black") + 
  labs(x = "Prokaryotic Order", y = "Log fold change", 
       title = "Log Fold Change in ANCOM Significant Taxa: Hyper Sensitive vs Resistant") + 
  theme_bw() + 
  theme(legend.position = "none",
        panel.grid.minor.y = element_blank()) + coord_flip() + scale_y_continuous(limits = c(-3, 3))
HS_R

#HS_SR
samp_frac = out$samp_frac
samp_frac[is.na(samp_frac)] = 0 
log_obs_abn = log(abundances(genus_data) + 1) 
log_obs_abn_adj = t(t(log_obs_abn) - samp_frac)
round(log_obs_abn_adj[, 1:6], 2) %>% 
  datatable(caption = "Bias-adjusted log observed abundances")
df_fig1 = data.frame(res$beta * res$diff_abn, check.names = FALSE) %>% 
  rownames_to_column("taxon_id")
df_fig2 = data.frame(res$se * res$diff_abn, check.names = FALSE) %>% 
  rownames_to_column("taxon_id")
colnames(df_fig2)[-1] = paste0(colnames(df_fig2)[-1], "SD")
df_fig = df_fig1 %>% left_join(df_fig2, by = "taxon_id") %>%
  transmute(taxon_id, `resitance_14_21Super Resistant`, `resitance_14_21Super ResistantSD`) %>% 
  filter(`resitance_14_21Super Resistant` != 0) %>% arrange(desc(`resitance_14_21Super Resistant`)) %>%
  mutate(group = ifelse(`resitance_14_21Super Resistant` > 0, "g1", "g2"))
df_fig$taxon_id = factor(df_fig$taxon_id, levels = df_fig$taxon_id)
HS_SR = ggplot(data = df_fig, 
           aes(x = taxon_id, y = `resitance_14_21Super Resistant`, fill = `resitance_14_21Super Resistant`, color = `resitance_14_21Super Resistant`)) + 
  geom_bar(stat = "identity", width = 0.7, 
           position = position_dodge(width = 0.4)) + scale_fill_viridis_c(option = "plasma") + scale_color_viridis_c(option = "plasma") +
  geom_errorbar(aes(ymin = `resitance_14_21Super Resistant` - `resitance_14_21Super ResistantSD`, ymax = `resitance_14_21Super Resistant` + `resitance_14_21Super ResistantSD`), width = 0.2,
                position = position_dodge(0.05), color = "black") + 
  labs(x = "Prokaryotic Order", y = "Log fold change", 
       title = "Log Fold Change in ANCOM Significant Taxa: Hyper Sensitive vs Super Resistant") + 
  theme_bw() + 
  theme(legend.position = "none",
        panel.grid.minor.y = element_blank()) + coord_flip() + scale_y_continuous(limits = c(-3, 3))
HS_SR


## Remove one group and Start from Sensitive
sens <- subset_samples(noport_bac, noport_bac@sam_data$resitance_14_21!="Hyper Sensitive")

genus_data = aggregate_taxa(sens, "Order")

out = ancombc(phyloseq = genus_data, formula = "resitance_14_21", 
              p_adj_method = "none", zero_cut = 0.90, lib_cut = 0, 
              group = "resitance_14_21", struc_zero = TRUE, neg_lb = TRUE, tol = 1e-5, 
              max_iter = 100, conserve = TRUE, alpha = 0.05, global = TRUE)

res = out$res
res_global = out$res_global

#S_R
samp_frac = out$samp_frac
samp_frac[is.na(samp_frac)] = 0 
log_obs_abn = log(abundances(genus_data) + 1) 
log_obs_abn_adj = t(t(log_obs_abn) - samp_frac)
round(log_obs_abn_adj[, 1:6], 2) %>% 
  datatable(caption = "Bias-adjusted log observed abundances")
df_fig1 = data.frame(res$beta * res$diff_abn, check.names = FALSE) %>% 
  rownames_to_column("taxon_id")

df_fig1$resitance_14_21Sensitive = df_fig1$resitance_14_21Sensitive*(-1)

df_fig2 = data.frame(res$se * res$diff_abn, check.names = FALSE) %>% 
  rownames_to_column("taxon_id")
colnames(df_fig2)[-1] = paste0(colnames(df_fig2)[-1], "SD")
df_fig = df_fig1 %>% left_join(df_fig2, by = "taxon_id") %>%
  transmute(taxon_id, `resitance_14_21Sensitive`, `resitance_14_21SensitiveSD`) %>% 
  filter(`resitance_14_21Sensitive` != 0) %>% arrange(desc(`resitance_14_21Sensitive`)) %>%
  mutate(group = ifelse(`resitance_14_21Sensitive` > 0, "g1", "g2"))
df_fig$taxon_id = factor(df_fig$taxon_id, levels = df_fig$taxon_id)

S_R = ggplot(data = df_fig, 
           aes(x = taxon_id, y = `resitance_14_21Sensitive`, fill = `resitance_14_21Sensitive`, color = `resitance_14_21Sensitive`)) + 
  geom_bar(stat = "identity", width = 0.7, 
           position = position_dodge(width = 0.4)) + scale_fill_viridis_c(option = "plasma") + scale_color_viridis_c(option = "plasma") +
  geom_errorbar(aes(ymin = `resitance_14_21Sensitive` - `resitance_14_21SensitiveSD`, ymax = `resitance_14_21Sensitive` + `resitance_14_21SensitiveSD`), width = 0.2,
                position = position_dodge(0.05), color = "black") + 
  labs(x = "Prokaryotic Order", y = "Log fold change", 
       title = "Log Fold Change in ANCOM Significant Taxa: Sensitive vs Resistant") + 
  theme_bw() + 
  theme(legend.position = "none",
        panel.grid.minor.y = element_blank()) + coord_flip() + scale_y_continuous(limits = c(-3, 3))
S_R

#T_R
samp_frac = out$samp_frac
samp_frac[is.na(samp_frac)] = 0 
log_obs_abn = log(abundances(genus_data) + 1) 
log_obs_abn_adj = t(t(log_obs_abn) - samp_frac)
round(log_obs_abn_adj[, 1:6], 2) %>% 
  datatable(caption = "Bias-adjusted log observed abundances")
df_fig1 = data.frame(res$beta * res$diff_abn, check.names = FALSE) %>% 
  rownames_to_column("taxon_id")

df_fig1$resitance_14_21Tolerant = df_fig1$resitance_14_21Tolerant*(-1)

df_fig2 = data.frame(res$se * res$diff_abn, check.names = FALSE) %>% 
  rownames_to_column("taxon_id")
colnames(df_fig2)[-1] = paste0(colnames(df_fig2)[-1], "SD")
df_fig = df_fig1 %>% left_join(df_fig2, by = "taxon_id") %>%
  transmute(taxon_id, `resitance_14_21Tolerant`, `resitance_14_21TolerantSD`) %>% 
  filter(`resitance_14_21Tolerant` != 0) %>% arrange(desc(`resitance_14_21Tolerant`)) %>%
  mutate(group = ifelse(`resitance_14_21Tolerant` > 0, "g1", "g2"))
df_fig$taxon_id = factor(df_fig$taxon_id, levels = df_fig$taxon_id)

T_R = ggplot(data = df_fig, 
           aes(x = taxon_id, y = `resitance_14_21Tolerant`, fill = `resitance_14_21Tolerant`, color = `resitance_14_21Tolerant`)) + 
  geom_bar(stat = "identity", width = 0.7, 
           position = position_dodge(width = 0.4)) + scale_fill_viridis_c(option = "plasma") + scale_color_viridis_c(option = "plasma") +
  geom_errorbar(aes(ymin = `resitance_14_21Tolerant` - `resitance_14_21TolerantSD`, ymax = `resitance_14_21Tolerant` + `resitance_14_21TolerantSD`), width = 0.2,
                position = position_dodge(0.05), color = "black") + 
  labs(x = "Prokaryotic Order", y = "Log fold change", 
       title = "Log Fold Change in ANCOM Significant Taxa: Tolerant vs Resistant") + 
  theme_bw() + 
  theme(legend.position = "none",
        panel.grid.minor.y = element_blank()) + coord_flip() + scale_y_continuous(limits = c(-3, 3))
T_R

#R_RS
samp_frac = out$samp_frac
samp_frac[is.na(samp_frac)] = 0 
log_obs_abn = log(abundances(genus_data) + 1) 
log_obs_abn_adj = t(t(log_obs_abn) - samp_frac)
round(log_obs_abn_adj[, 1:6], 2) %>% 
  datatable(caption = "Bias-adjusted log observed abundances")
df_fig1 = data.frame(res$beta * res$diff_abn, check.names = FALSE) %>% 
  rownames_to_column("taxon_id")
df_fig2 = data.frame(res$se * res$diff_abn, check.names = FALSE) %>% 
  rownames_to_column("taxon_id")
colnames(df_fig2)[-1] = paste0(colnames(df_fig2)[-1], "SD")
df_fig = df_fig1 %>% left_join(df_fig2, by = "taxon_id") %>%
  transmute(taxon_id, `resitance_14_21Super Resistant`, `resitance_14_21Super ResistantSD`) %>% 
  filter(`resitance_14_21Super Resistant` != 0) %>% arrange(desc(`resitance_14_21Super Resistant`)) %>%
  mutate(group = ifelse(`resitance_14_21Super Resistant` > 0, "g1", "g2"))
df_fig$taxon_id = factor(df_fig$taxon_id, levels = df_fig$taxon_id)
R_RS = ggplot(data = df_fig, 
           aes(x = taxon_id, y = `resitance_14_21Super Resistant`, fill = `resitance_14_21Super Resistant`, color = `resitance_14_21Super Resistant`)) + 
  geom_bar(stat = "identity", width = 0.7, 
           position = position_dodge(width = 0.4)) + scale_fill_viridis_c(option = "plasma") + scale_color_viridis_c(option = "plasma") +
  geom_errorbar(aes(ymin = `resitance_14_21Super Resistant` - `resitance_14_21Super ResistantSD`, ymax = `resitance_14_21Super Resistant` + `resitance_14_21Super ResistantSD`), width = 0.2,
                position = position_dodge(0.05), color = "black") + 
  labs(x = "Prokaryotic Order", y = "Log fold change", 
       title = "Log Fold Change in ANCOM Significant Taxa: Resistant vs Super Resistant") + 
  theme_bw() + 
  theme(legend.position = "none",
        panel.grid.minor.y = element_blank()) + coord_flip() + scale_y_continuous(limits = c(-3, 3))
R_RS

## Remove Resistant group now
resis <- subset_samples(sens, sens@sam_data$resitance_14_21!="Resistant")

genus_data = aggregate_taxa(resis, "Order")

out = ancombc(phyloseq = genus_data, formula = "resitance_14_21", 
              p_adj_method = "none", zero_cut = 0.90, lib_cut = 0, 
              group = "resitance_14_21", struc_zero = TRUE, neg_lb = TRUE, tol = 1e-5, 
              max_iter = 100, conserve = TRUE, alpha = 0.05, global = TRUE)

res = out$res
res_global = out$res_global

#S_T
samp_frac = out$samp_frac
samp_frac[is.na(samp_frac)] = 0 
log_obs_abn = log(abundances(genus_data) + 1) 
log_obs_abn_adj = t(t(log_obs_abn) - samp_frac)
round(log_obs_abn_adj[, 1:6], 2) %>% 
  datatable(caption = "Bias-adjusted log observed abundances")
df_fig1 = data.frame(res$beta * res$diff_abn, check.names = FALSE) %>% 
  rownames_to_column("taxon_id")
df_fig2 = data.frame(res$se * res$diff_abn, check.names = FALSE) %>% 
  rownames_to_column("taxon_id")
colnames(df_fig2)[-1] = paste0(colnames(df_fig2)[-1], "SD")
df_fig = df_fig1 %>% left_join(df_fig2, by = "taxon_id") %>%
  transmute(taxon_id, `resitance_14_21Tolerant`, `resitance_14_21TolerantSD`) %>% 
  filter(`resitance_14_21Tolerant` != 0) %>% arrange(desc(`resitance_14_21Tolerant`)) %>%
  mutate(group = ifelse(`resitance_14_21Tolerant` > 0, "g1", "g2"))
df_fig$taxon_id = factor(df_fig$taxon_id, levels = df_fig$taxon_id)
S_T = ggplot(data = df_fig, 
           aes(x = taxon_id, y = `resitance_14_21Tolerant`, fill = `resitance_14_21Tolerant`, color = `resitance_14_21Tolerant`)) + 
  geom_bar(stat = "identity", width = 0.7, 
           position = position_dodge(width = 0.4)) + scale_fill_viridis_c(option = "plasma") + scale_color_viridis_c(option = "plasma") +
  geom_errorbar(aes(ymin = `resitance_14_21Tolerant` - `resitance_14_21TolerantSD`, ymax = `resitance_14_21Tolerant` + `resitance_14_21TolerantSD`), width = 0.2,
                position = position_dodge(0.05), color = "black") + 
  labs(x = "Prokaryotic Order", y = "Log fold change", 
       title = "Log Fold Change in ANCOM Significant Taxa: Sensitive vs Tolerant") + 
  theme_bw() + 
  theme(legend.position = "none",
        panel.grid.minor.y = element_blank()) + coord_flip() + scale_y_continuous(limits = c(-3, 3))
S_T

#S_SR
samp_frac = out$samp_frac
samp_frac[is.na(samp_frac)] = 0 
log_obs_abn = log(abundances(genus_data) + 1) 
log_obs_abn_adj = t(t(log_obs_abn) - samp_frac)
round(log_obs_abn_adj[, 1:6], 2) %>% 
  datatable(caption = "Bias-adjusted log observed abundances")
df_fig1 = data.frame(res$beta * res$diff_abn, check.names = FALSE) %>% 
  rownames_to_column("taxon_id")
df_fig2 = data.frame(res$se * res$diff_abn, check.names = FALSE) %>% 
  rownames_to_column("taxon_id")
colnames(df_fig2)[-1] = paste0(colnames(df_fig2)[-1], "SD")
df_fig = df_fig1 %>% left_join(df_fig2, by = "taxon_id") %>%
  transmute(taxon_id, `resitance_14_21Super Resistant`, `resitance_14_21Super ResistantSD`) %>% 
  filter(`resitance_14_21Super Resistant` != 0) %>% arrange(desc(`resitance_14_21Super Resistant`)) %>%
  mutate(group = ifelse(`resitance_14_21Super Resistant` > 0, "g1", "g2"))
df_fig$taxon_id = factor(df_fig$taxon_id, levels = df_fig$taxon_id)
S_SR = ggplot(data = df_fig, 
           aes(x = taxon_id, y = `resitance_14_21Super Resistant`, fill = `resitance_14_21Super Resistant`, color = `resitance_14_21Super Resistant`)) + 
  geom_bar(stat = "identity", width = 0.7, 
           position = position_dodge(width = 0.4)) + scale_fill_viridis_c(option = "plasma") + scale_color_viridis_c(option = "plasma") +
  geom_errorbar(aes(ymin = `resitance_14_21Super Resistant` - `resitance_14_21Super ResistantSD`, ymax = `resitance_14_21Super Resistant` + `resitance_14_21Super ResistantSD`), width = 0.2,
                position = position_dodge(0.05), color = "black") + 
  labs(x = "Prokaryotic Order", y = "Log fold change", 
       title = "Log Fold Change in ANCOM Significant Taxa: Sensitive vs Super Resistant") + 
  theme_bw() + 
  theme(legend.position = "none",
        panel.grid.minor.y = element_blank()) + coord_flip() + scale_y_continuous(limits = c(-3, 3))
S_SR

## Remove Sensitive
lastone <- subset_samples(resis, resis@sam_data$resitance_14_21!="Sensitive")
genus_data = aggregate_taxa(lastone, "Order")

out = ancombc(phyloseq = genus_data, formula = "resitance_14_21", 
              p_adj_method = "none", zero_cut = 0.90, lib_cut = 0, 
              group = "resitance_14_21", struc_zero = TRUE, neg_lb = TRUE, tol = 1e-5, 
              max_iter = 100, conserve = TRUE, alpha = 0.05, global = TRUE)

res = out$res
res_global = out$res_global

#T_SR
samp_frac = out$samp_frac
samp_frac[is.na(samp_frac)] = 0 
log_obs_abn = log(abundances(genus_data) + 1) 
log_obs_abn_adj = t(t(log_obs_abn) - samp_frac)
round(log_obs_abn_adj[, 1:6], 2) %>% 
  datatable(caption = "Bias-adjusted log observed abundances")
df_fig1 = data.frame(res$beta * res$diff_abn, check.names = FALSE) %>% 
  rownames_to_column("taxon_id")

df_fig1$resitance_14_21Tolerant = df_fig1$resitance_14_21Tolerant*(-1)

df_fig2 = data.frame(res$se * res$diff_abn, check.names = FALSE) %>% 
  rownames_to_column("taxon_id")
colnames(df_fig2)[-1] = paste0(colnames(df_fig2)[-1], "SD")
df_fig = df_fig1 %>% left_join(df_fig2, by = "taxon_id") %>%
  transmute(taxon_id, `resitance_14_21Tolerant`, `resitance_14_21TolerantSD`) %>% 
  filter(`resitance_14_21Tolerant` != 0) %>% arrange(desc(`resitance_14_21Tolerant`)) %>%
  mutate(group = ifelse(`resitance_14_21Tolerant` > 0, "g1", "g2"))
df_fig$taxon_id = factor(df_fig$taxon_id, levels = df_fig$taxon_id)

T_SR = ggplot(data = df_fig, 
           aes(x = taxon_id, y = `resitance_14_21Tolerant`, fill = `resitance_14_21Tolerant`, color = `resitance_14_21Tolerant`)) + 
  geom_bar(stat = "identity", width = 0.7, 
           position = position_dodge(width = 0.4)) + scale_fill_viridis_c(option = "plasma") + scale_color_viridis_c(option = "plasma") +
  geom_errorbar(aes(ymin = `resitance_14_21Tolerant` - `resitance_14_21TolerantSD`, ymax = `resitance_14_21Tolerant` + `resitance_14_21TolerantSD`), width = 0.2,
                position = position_dodge(0.05), color = "black") + 
  labs(x = "Prokaryotic Order", y = "Log fold change", 
       title = "Log Fold Change in ANCOM Significant Taxa: Tolerant vs Super Resistant ") + 
  theme_bw() + 
  theme(legend.position = "none",
        panel.grid.minor.y = element_blank()) + coord_flip() + scale_y_continuous(limits = c(-3, 3))
T_SR

library("ggpubr")
pdf("/Volumes/GoogleDrive/.shortcut-targets-by-id/1NZWDX6hj2iMLlcMpeA9ILkNyhxyngfoM/Bonacolta\ et\ al.\ 2020\ Paramuricea/manuscript/figures/main\ figs/raw/Fig9S-ANCOM-BAC.pdf", width=9, height=25)
ggarrange(HS_S, HS_T, HS_R, HS_SR, S_T, S_R, S_SR, T_R, T_SR, R_RS, nrow=10, common.legend = TRUE, legend="none")

dev.off()
```
### Fig10S: Grid of ANCOMBC-LFC for Eukaryotic Orders
```{r}
library(ANCOMBC)
library(DT)

oldtax <- data.frame(tax_table(noport))

oldtax$Order[oldtax$Order == "Dinophyceae_X"] <- "Dinophyceae IS"
oldtax$Order[oldtax$Order == "Prymnesiophyceae_X"] <- "Prymnesiophyceae IS"
oldtax$Order[oldtax$Order == "Prasino-Clade-9_NA"] <- "Prasino-Clade-9 IS"
oldtax$Order[oldtax$Order == "Apicomplexa_X"] <- "Apicomplexa IS"
oldtax$Order[oldtax$Order == "Dinoflagellata_X"] <- "Dinoflagellata IS"
oldtax$Order[oldtax$Order == "Coccidiomorphea_NA"] <- "Coccidiomorphea IS"
oldtax$Order[oldtax$Order == "Alveolata_X"] <- "Alveolata IS"
oldtax$Order[oldtax$Order == "Dinophyceae_NA"] <- "Dinophyceae IS"
oldtax$Order[oldtax$Order == "Eukaryota_X"] <- "Eukaryota IS"
oldtax$Order[oldtax$Order == "Dinophyceae_NA"] <- "Dinophyceae IS"
oldtax$Order[oldtax$Order == "Prymnesiophyceae_NA"] <- "Prymnesiophyceae IS"
oldtax$Order[oldtax$Order == "Prasino-Clade-9_X"] <- "Prasino-Clade-9 IS"
oldtax$Order[oldtax$Order == "Apicomplexa_NA"] <- "Apicomplexa IS"
oldtax$Order[oldtax$Order == "Dinoflagellata_NA"] <- "Dinoflagellata IS"
oldtax$Order[oldtax$Order == "Coccidiomorphea_X"] <- "Coccidiomorphea IS"
oldtax$Order[oldtax$Order == "Alveolata_NA"] <- "Alveolata IS"
oldtax$Order[oldtax$Order == "Dinophyceae_X"] <- "Dinophyceae IS"
oldtax$Order[oldtax$Order == "Eukaryota_NA"] <- "Eukaryota IS"
oldtax$Order[oldtax$Order == "Phyllopharyngea_NA"] <- "Phyllopharyngea IS"
oldtax$Order[oldtax$Order == "Syndiniales_X"] <- "Syndiniales IS"
oldtax$Order[oldtax$Order == "Syndiniales_NA"] <- "Syndiniales IS"

tax_table(noport) <- as.matrix(oldtax)
genus_data = aggregate_taxa(noport, "Order")

out = ancombc(phyloseq = genus_data, formula = "resitance_14_21", 
              p_adj_method = "none", zero_cut = 0.90, lib_cut = 0, 
              group = "resitance_14_21", struc_zero = TRUE, neg_lb = TRUE, tol = 1e-5, 
              max_iter = 100, conserve = TRUE, alpha = 0.05, global = TRUE)

res = out$res
res_global = out$res_global

#HS_S
samp_frac = out$samp_frac
samp_frac[is.na(samp_frac)] = 0 
log_obs_abn = log(abundances(genus_data) + 1) 
log_obs_abn_adj = t(t(log_obs_abn) - samp_frac)
round(log_obs_abn_adj[, 1:6], 2) %>% 
  datatable(caption = "Bias-adjusted log observed abundances")
df_fig1 = data.frame(res$beta * res$diff_abn, check.names = FALSE) %>% 
  rownames_to_column("taxon_id")
df_fig2 = data.frame(res$se * res$diff_abn, check.names = FALSE) %>% 
  rownames_to_column("taxon_id")
colnames(df_fig2)[-1] = paste0(colnames(df_fig2)[-1], "SD")
df_fig = df_fig1 %>% left_join(df_fig2, by = "taxon_id") %>%
  transmute(taxon_id, resitance_14_21Sensitive, resitance_14_21SensitiveSD) %>% 
  filter(resitance_14_21Sensitive != 0) %>% arrange(desc(resitance_14_21Sensitive)) %>%
  mutate(group = ifelse(resitance_14_21Sensitive > 0, "g1", "g2"))
df_fig$taxon_id = factor(df_fig$taxon_id, levels = df_fig$taxon_id)
HS_S = ggplot(data = df_fig, 
           aes(x = taxon_id, y = resitance_14_21Sensitive, fill = resitance_14_21Sensitive, color = resitance_14_21Sensitive)) + 
  geom_bar(stat = "identity", width = 0.7, 
           position = position_dodge(width = 0.4)) + scale_fill_viridis_c(option = "plasma") + scale_color_viridis_c(option = "plasma") +
  geom_errorbar(aes(ymin = resitance_14_21Sensitive - resitance_14_21SensitiveSD, ymax = resitance_14_21Sensitive + resitance_14_21SensitiveSD), width = 0.2,
                position = position_dodge(0.05), color = "black") + 
  labs(x = "Eukaryotic Order", y = "Log fold change", 
       title = "Log Fold Change in ANCOM Significant Taxa: Hyper Sensitive vs Sensitive") + 
  theme_bw() + 
  theme(legend.position = "none",
        panel.grid.minor.y = element_blank()) + coord_flip() + scale_y_continuous(limits = c(-3, 3))
HS_S

#HS_T
samp_frac = out$samp_frac
samp_frac[is.na(samp_frac)] = 0 
log_obs_abn = log(abundances(genus_data) + 1) 
log_obs_abn_adj = t(t(log_obs_abn) - samp_frac)
round(log_obs_abn_adj[, 1:6], 2) %>% 
  datatable(caption = "Bias-adjusted log observed abundances")
df_fig1 = data.frame(res$beta * res$diff_abn, check.names = FALSE) %>% 
  rownames_to_column("taxon_id")
df_fig2 = data.frame(res$se * res$diff_abn, check.names = FALSE) %>% 
  rownames_to_column("taxon_id")
colnames(df_fig2)[-1] = paste0(colnames(df_fig2)[-1], "SD")
df_fig = df_fig1 %>% left_join(df_fig2, by = "taxon_id") %>%
  transmute(taxon_id, resitance_14_21Tolerant, resitance_14_21TolerantSD) %>% 
  filter(resitance_14_21Tolerant != 0) %>% arrange(desc(resitance_14_21Tolerant)) %>%
  mutate(group = ifelse(resitance_14_21Tolerant > 0, "g1", "g2"))
df_fig$taxon_id = factor(df_fig$taxon_id, levels = df_fig$taxon_id)
HS_T = ggplot(data = df_fig, 
           aes(x = taxon_id, y = resitance_14_21Tolerant, fill = resitance_14_21Tolerant, color = resitance_14_21Tolerant)) + 
  geom_bar(stat = "identity", width = 0.7, 
           position = position_dodge(width = 0.4)) + scale_fill_viridis_c(option = "plasma") + scale_color_viridis_c(option = "plasma") +
  geom_errorbar(aes(ymin = resitance_14_21Tolerant - resitance_14_21TolerantSD, ymax = resitance_14_21Tolerant + resitance_14_21TolerantSD), width = 0.2,
                position = position_dodge(0.05), color = "black") + 
  labs(x = "Eukaryotic Order", y = "Log fold change", 
       title = "Log Fold Change in ANCOM Significant Taxa: Hyper Sensitive vs Tolerant") + 
  theme_bw() + 
  theme(legend.position = "none",
        panel.grid.minor.y = element_blank()) + coord_flip() + scale_y_continuous(limits = c(-3, 3))
HS_T

#HS_R
samp_frac = out$samp_frac
samp_frac[is.na(samp_frac)] = 0 
log_obs_abn = log(abundances(genus_data) + 1) 
log_obs_abn_adj = t(t(log_obs_abn) - samp_frac)
round(log_obs_abn_adj[, 1:6], 2) %>% 
  datatable(caption = "Bias-adjusted log observed abundances")
df_fig1 = data.frame(res$beta * res$diff_abn, check.names = FALSE) %>% 
  rownames_to_column("taxon_id")
df_fig2 = data.frame(res$se * res$diff_abn, check.names = FALSE) %>% 
  rownames_to_column("taxon_id")
colnames(df_fig2)[-1] = paste0(colnames(df_fig2)[-1], "SD")
df_fig = df_fig1 %>% left_join(df_fig2, by = "taxon_id") %>%
  transmute(taxon_id, resitance_14_21Resistant, resitance_14_21ResistantSD) %>% 
  filter(resitance_14_21Resistant != 0) %>% arrange(desc(resitance_14_21Resistant)) %>%
  mutate(group = ifelse(resitance_14_21Resistant > 0, "g1", "g2"))
df_fig$taxon_id = factor(df_fig$taxon_id, levels = df_fig$taxon_id)
HS_R = ggplot(data = df_fig, 
           aes(x = taxon_id, y = resitance_14_21Resistant, fill = resitance_14_21Resistant, color = resitance_14_21Resistant)) + 
  geom_bar(stat = "identity", width = 0.7, 
           position = position_dodge(width = 0.4)) + scale_fill_viridis_c(option = "plasma") + scale_color_viridis_c(option = "plasma") +
  geom_errorbar(aes(ymin = resitance_14_21Resistant - resitance_14_21ResistantSD, ymax = resitance_14_21Resistant + resitance_14_21ResistantSD), width = 0.2,
                position = position_dodge(0.05), color = "black") + 
  labs(x = "Eukaryotic Order", y = "Log fold change", 
       title = "Log Fold Change in ANCOM Significant Taxa: Hyper Sensitive vs Resistant") + 
  theme_bw() + 
  theme(legend.position = "none",
        panel.grid.minor.y = element_blank()) + coord_flip() + scale_y_continuous(limits = c(-3, 3))
HS_R

#HS_SR
samp_frac = out$samp_frac
samp_frac[is.na(samp_frac)] = 0 
log_obs_abn = log(abundances(genus_data) + 1) 
log_obs_abn_adj = t(t(log_obs_abn) - samp_frac)
round(log_obs_abn_adj[, 1:6], 2) %>% 
  datatable(caption = "Bias-adjusted log observed abundances")
df_fig1 = data.frame(res$beta * res$diff_abn, check.names = FALSE) %>% 
  rownames_to_column("taxon_id")
df_fig2 = data.frame(res$se * res$diff_abn, check.names = FALSE) %>% 
  rownames_to_column("taxon_id")
colnames(df_fig2)[-1] = paste0(colnames(df_fig2)[-1], "SD")
df_fig = df_fig1 %>% left_join(df_fig2, by = "taxon_id") %>%
  transmute(taxon_id, `resitance_14_21Super Resistant`, `resitance_14_21Super ResistantSD`) %>% 
  filter(`resitance_14_21Super Resistant` != 0) %>% arrange(desc(`resitance_14_21Super Resistant`)) %>%
  mutate(group = ifelse(`resitance_14_21Super Resistant` > 0, "g1", "g2"))
df_fig$taxon_id = factor(df_fig$taxon_id, levels = df_fig$taxon_id)
HS_SR = ggplot(data = df_fig, 
           aes(x = taxon_id, y = `resitance_14_21Super Resistant`, fill = `resitance_14_21Super Resistant`, color = `resitance_14_21Super Resistant`)) + 
  geom_bar(stat = "identity", width = 0.7, 
           position = position_dodge(width = 0.4)) + scale_fill_viridis_c(option = "plasma") + scale_color_viridis_c(option = "plasma") +
  geom_errorbar(aes(ymin = `resitance_14_21Super Resistant` - `resitance_14_21Super ResistantSD`, ymax = `resitance_14_21Super Resistant` + `resitance_14_21Super ResistantSD`), width = 0.2,
                position = position_dodge(0.05), color = "black") + 
  labs(x = "Eukaryotic Order", y = "Log fold change", 
       title = "Log Fold Change in ANCOM Significant Taxa: Hyper Sensitive vs Super Resistant") + 
  theme_bw() + 
  theme(legend.position = "none",
        panel.grid.minor.y = element_blank()) + coord_flip() + scale_y_continuous(limits = c(-3, 3))
HS_SR


## Remove one group and Start from Sensitive
sens <- subset_samples(noport, noport@sam_data$resitance_14_21!="Hyper Sensitive")

genus_data = aggregate_taxa(sens, "Order")

out = ancombc(phyloseq = genus_data, formula = "resitance_14_21", 
              p_adj_method = "none", zero_cut = 0.90, lib_cut = 0, 
              group = "resitance_14_21", struc_zero = TRUE, neg_lb = TRUE, tol = 1e-5, 
              max_iter = 100, conserve = TRUE, alpha = 0.05, global = TRUE)

res = out$res
res_global = out$res_global

#S_R
samp_frac = out$samp_frac
samp_frac[is.na(samp_frac)] = 0 
log_obs_abn = log(abundances(genus_data) + 1) 
log_obs_abn_adj = t(t(log_obs_abn) - samp_frac)
round(log_obs_abn_adj[, 1:6], 2) %>% 
  datatable(caption = "Bias-adjusted log observed abundances")
df_fig1 = data.frame(res$beta * res$diff_abn, check.names = FALSE) %>% 
  rownames_to_column("taxon_id")

df_fig1$resitance_14_21Sensitive = df_fig1$resitance_14_21Sensitive*(-1)

df_fig2 = data.frame(res$se * res$diff_abn, check.names = FALSE) %>% 
  rownames_to_column("taxon_id")
colnames(df_fig2)[-1] = paste0(colnames(df_fig2)[-1], "SD")
df_fig = df_fig1 %>% left_join(df_fig2, by = "taxon_id") %>%
  transmute(taxon_id, `resitance_14_21Sensitive`, `resitance_14_21SensitiveSD`) %>% 
  filter(`resitance_14_21Sensitive` != 0) %>% arrange(desc(`resitance_14_21Sensitive`)) %>%
  mutate(group = ifelse(`resitance_14_21Sensitive` > 0, "g1", "g2"))
df_fig$taxon_id = factor(df_fig$taxon_id, levels = df_fig$taxon_id)

S_R = ggplot(data = df_fig, 
           aes(x = taxon_id, y = `resitance_14_21Sensitive`, fill = `resitance_14_21Sensitive`, color = `resitance_14_21Sensitive`)) + 
  geom_bar(stat = "identity", width = 0.7, 
           position = position_dodge(width = 0.4)) + scale_fill_viridis_c(option = "plasma") + scale_color_viridis_c(option = "plasma") +
  geom_errorbar(aes(ymin = `resitance_14_21Sensitive` - `resitance_14_21SensitiveSD`, ymax = `resitance_14_21Sensitive` + `resitance_14_21SensitiveSD`), width = 0.2,
                position = position_dodge(0.05), color = "black") + 
  labs(x = "Eukaryotic Order", y = "Log fold change", 
       title = "Log Fold Change in ANCOM Significant Taxa: Sensitive vs Resistant") + 
  theme_bw() + 
  theme(legend.position = "none",
        panel.grid.minor.y = element_blank()) + coord_flip() + scale_y_continuous(limits = c(-3, 3))
S_R

#T_R
samp_frac = out$samp_frac
samp_frac[is.na(samp_frac)] = 0 
log_obs_abn = log(abundances(genus_data) + 1) 
log_obs_abn_adj = t(t(log_obs_abn) - samp_frac)
round(log_obs_abn_adj[, 1:6], 2) %>% 
  datatable(caption = "Bias-adjusted log observed abundances")
df_fig1 = data.frame(res$beta * res$diff_abn, check.names = FALSE) %>% 
  rownames_to_column("taxon_id")

df_fig1$resitance_14_21Tolerant = df_fig1$resitance_14_21Tolerant*(-1)

df_fig2 = data.frame(res$se * res$diff_abn, check.names = FALSE) %>% 
  rownames_to_column("taxon_id")
colnames(df_fig2)[-1] = paste0(colnames(df_fig2)[-1], "SD")
df_fig = df_fig1 %>% left_join(df_fig2, by = "taxon_id") %>%
  transmute(taxon_id, `resitance_14_21Tolerant`, `resitance_14_21TolerantSD`) %>% 
  filter(`resitance_14_21Tolerant` != 0) %>% arrange(desc(`resitance_14_21Tolerant`)) %>%
  mutate(group = ifelse(`resitance_14_21Tolerant` > 0, "g1", "g2"))
df_fig$taxon_id = factor(df_fig$taxon_id, levels = df_fig$taxon_id)

T_R = ggplot(data = df_fig, 
           aes(x = taxon_id, y = `resitance_14_21Tolerant`, fill = `resitance_14_21Tolerant`, color = `resitance_14_21Tolerant`)) + 
  geom_bar(stat = "identity", width = 0.7, 
           position = position_dodge(width = 0.4)) + scale_fill_viridis_c(option = "plasma") + scale_color_viridis_c(option = "plasma") +
  geom_errorbar(aes(ymin = `resitance_14_21Tolerant` - `resitance_14_21TolerantSD`, ymax = `resitance_14_21Tolerant` + `resitance_14_21TolerantSD`), width = 0.2,
                position = position_dodge(0.05), color = "black") + 
  labs(x = "Eukaryotic Order", y = "Log fold change", 
       title = "Log Fold Change in ANCOM Significant Taxa: Tolerant vs Resistant") + 
  theme_bw() + 
  theme(legend.position = "none",
        panel.grid.minor.y = element_blank()) + coord_flip() + scale_y_continuous(limits = c(-3, 3))
T_R

#R_RS
samp_frac = out$samp_frac
samp_frac[is.na(samp_frac)] = 0 
log_obs_abn = log(abundances(genus_data) + 1) 
log_obs_abn_adj = t(t(log_obs_abn) - samp_frac)
round(log_obs_abn_adj[, 1:6], 2) %>% 
  datatable(caption = "Bias-adjusted log observed abundances")
df_fig1 = data.frame(res$beta * res$diff_abn, check.names = FALSE) %>% 
  rownames_to_column("taxon_id")
df_fig2 = data.frame(res$se * res$diff_abn, check.names = FALSE) %>% 
  rownames_to_column("taxon_id")
colnames(df_fig2)[-1] = paste0(colnames(df_fig2)[-1], "SD")
df_fig = df_fig1 %>% left_join(df_fig2, by = "taxon_id") %>%
  transmute(taxon_id, `resitance_14_21Super Resistant`, `resitance_14_21Super ResistantSD`) %>% 
  filter(`resitance_14_21Super Resistant` != 0) %>% arrange(desc(`resitance_14_21Super Resistant`)) %>%
  mutate(group = ifelse(`resitance_14_21Super Resistant` > 0, "g1", "g2"))
df_fig$taxon_id = factor(df_fig$taxon_id, levels = df_fig$taxon_id)
R_RS = ggplot(data = df_fig, 
           aes(x = taxon_id, y = `resitance_14_21Super Resistant`, fill = `resitance_14_21Super Resistant`, color = `resitance_14_21Super Resistant`)) + 
  geom_bar(stat = "identity", width = 0.7, 
           position = position_dodge(width = 0.4)) + scale_fill_viridis_c(option = "plasma") + scale_color_viridis_c(option = "plasma") +
  geom_errorbar(aes(ymin = `resitance_14_21Super Resistant` - `resitance_14_21Super ResistantSD`, ymax = `resitance_14_21Super Resistant` + `resitance_14_21Super ResistantSD`), width = 0.2,
                position = position_dodge(0.05), color = "black") + 
  labs(x = "Eukaryotic Order", y = "Log fold change", 
       title = "Log Fold Change in ANCOM Significant Taxa: Resistant vs Super Resistant") + 
  theme_bw() + 
  theme(legend.position = "none",
        panel.grid.minor.y = element_blank()) + coord_flip() + scale_y_continuous(limits = c(-3, 3))
R_RS

## Remove Resistant group now
resis <- subset_samples(sens, sens@sam_data$resitance_14_21!="Resistant")

genus_data = aggregate_taxa(resis, "Order")

out = ancombc(phyloseq = genus_data, formula = "resitance_14_21", 
              p_adj_method = "none", zero_cut = 0.90, lib_cut = 0, 
              group = "resitance_14_21", struc_zero = TRUE, neg_lb = TRUE, tol = 1e-5, 
              max_iter = 100, conserve = TRUE, alpha = 0.05, global = TRUE)

res = out$res
res_global = out$res_global

#S_T
samp_frac = out$samp_frac
samp_frac[is.na(samp_frac)] = 0 
log_obs_abn = log(abundances(genus_data) + 1) 
log_obs_abn_adj = t(t(log_obs_abn) - samp_frac)
round(log_obs_abn_adj[, 1:6], 2) %>% 
  datatable(caption = "Bias-adjusted log observed abundances")
df_fig1 = data.frame(res$beta * res$diff_abn, check.names = FALSE) %>% 
  rownames_to_column("taxon_id")
df_fig2 = data.frame(res$se * res$diff_abn, check.names = FALSE) %>% 
  rownames_to_column("taxon_id")
colnames(df_fig2)[-1] = paste0(colnames(df_fig2)[-1], "SD")
df_fig = df_fig1 %>% left_join(df_fig2, by = "taxon_id") %>%
  transmute(taxon_id, `resitance_14_21Tolerant`, `resitance_14_21TolerantSD`) %>% 
  filter(`resitance_14_21Tolerant` != 0) %>% arrange(desc(`resitance_14_21Tolerant`)) %>%
  mutate(group = ifelse(`resitance_14_21Tolerant` > 0, "g1", "g2"))
df_fig$taxon_id = factor(df_fig$taxon_id, levels = df_fig$taxon_id)
S_T = ggplot(data = df_fig, 
           aes(x = taxon_id, y = `resitance_14_21Tolerant`, fill = `resitance_14_21Tolerant`, color = `resitance_14_21Tolerant`)) + 
  geom_bar(stat = "identity", width = 0.7, 
           position = position_dodge(width = 0.4)) + scale_fill_viridis_c(option = "plasma") + scale_color_viridis_c(option = "plasma") +
  geom_errorbar(aes(ymin = `resitance_14_21Tolerant` - `resitance_14_21TolerantSD`, ymax = `resitance_14_21Tolerant` + `resitance_14_21TolerantSD`), width = 0.2,
                position = position_dodge(0.05), color = "black") + 
  labs(x = "Eukaryotic Order", y = "Log fold change", 
       title = "Log Fold Change in ANCOM Significant Taxa: Sensitive vs Tolerant") + 
  theme_bw() + 
  theme(legend.position = "none",
        panel.grid.minor.y = element_blank()) + coord_flip() + scale_y_continuous(limits = c(-3, 3))
S_T

#S_SR
samp_frac = out$samp_frac
samp_frac[is.na(samp_frac)] = 0 
log_obs_abn = log(abundances(genus_data) + 1) 
log_obs_abn_adj = t(t(log_obs_abn) - samp_frac)
round(log_obs_abn_adj[, 1:6], 2) %>% 
  datatable(caption = "Bias-adjusted log observed abundances")
df_fig1 = data.frame(res$beta * res$diff_abn, check.names = FALSE) %>% 
  rownames_to_column("taxon_id")
df_fig2 = data.frame(res$se * res$diff_abn, check.names = FALSE) %>% 
  rownames_to_column("taxon_id")
colnames(df_fig2)[-1] = paste0(colnames(df_fig2)[-1], "SD")
df_fig = df_fig1 %>% left_join(df_fig2, by = "taxon_id") %>%
  transmute(taxon_id, `resitance_14_21Super Resistant`, `resitance_14_21Super ResistantSD`) %>% 
  filter(`resitance_14_21Super Resistant` != 0) %>% arrange(desc(`resitance_14_21Super Resistant`)) %>%
  mutate(group = ifelse(`resitance_14_21Super Resistant` > 0, "g1", "g2"))
df_fig$taxon_id = factor(df_fig$taxon_id, levels = df_fig$taxon_id)
S_SR = ggplot(data = df_fig, 
           aes(x = taxon_id, y = `resitance_14_21Super Resistant`, fill = `resitance_14_21Super Resistant`, color = `resitance_14_21Super Resistant`)) + 
  geom_bar(stat = "identity", width = 0.7, 
           position = position_dodge(width = 0.4)) + scale_fill_viridis_c(option = "plasma") + scale_color_viridis_c(option = "plasma") +
  geom_errorbar(aes(ymin = `resitance_14_21Super Resistant` - `resitance_14_21Super ResistantSD`, ymax = `resitance_14_21Super Resistant` + `resitance_14_21Super ResistantSD`), width = 0.2,
                position = position_dodge(0.05), color = "black") + 
  labs(x = "Eukaryotic Order", y = "Log fold change", 
       title = "Log Fold Change in ANCOM Significant Taxa: Sensitive vs Super Resistant") + 
  theme_bw() + 
  theme(legend.position = "none",
        panel.grid.minor.y = element_blank()) + coord_flip() + scale_y_continuous(limits = c(-3, 3))
S_SR

## Remove Sensitive
lastone <- subset_samples(resis, resis@sam_data$resitance_14_21!="Sensitive")
genus_data = aggregate_taxa(lastone, "Order")

out = ancombc(phyloseq = genus_data, formula = "resitance_14_21", 
              p_adj_method = "none", zero_cut = 0.90, lib_cut = 0, 
              group = "resitance_14_21", struc_zero = TRUE, neg_lb = TRUE, tol = 1e-5, 
              max_iter = 100, conserve = TRUE, alpha = 0.05, global = TRUE)

res = out$res
res_global = out$res_global

#T_SR
samp_frac = out$samp_frac
samp_frac[is.na(samp_frac)] = 0 
log_obs_abn = log(abundances(genus_data) + 1) 
log_obs_abn_adj = t(t(log_obs_abn) - samp_frac)
round(log_obs_abn_adj[, 1:6], 2) %>% 
  datatable(caption = "Bias-adjusted log observed abundances")
df_fig1 = data.frame(res$beta * res$diff_abn, check.names = FALSE) %>% 
  rownames_to_column("taxon_id")

df_fig1$resitance_14_21Tolerant = df_fig1$resitance_14_21Tolerant*(-1)

df_fig2 = data.frame(res$se * res$diff_abn, check.names = FALSE) %>% 
  rownames_to_column("taxon_id")
colnames(df_fig2)[-1] = paste0(colnames(df_fig2)[-1], "SD")
df_fig = df_fig1 %>% left_join(df_fig2, by = "taxon_id") %>%
  transmute(taxon_id, `resitance_14_21Tolerant`, `resitance_14_21TolerantSD`) %>% 
  filter(`resitance_14_21Tolerant` != 0) %>% arrange(desc(`resitance_14_21Tolerant`)) %>%
  mutate(group = ifelse(`resitance_14_21Tolerant` > 0, "g1", "g2"))
df_fig$taxon_id = factor(df_fig$taxon_id, levels = df_fig$taxon_id)

T_SR = ggplot(data = df_fig, 
           aes(x = taxon_id, y = `resitance_14_21Tolerant`, fill = `resitance_14_21Tolerant`, color = `resitance_14_21Tolerant`)) + 
  geom_bar(stat = "identity", width = 0.7, 
           position = position_dodge(width = 0.4)) + scale_fill_viridis_c(option = "plasma") + scale_color_viridis_c(option = "plasma") +
  geom_errorbar(aes(ymin = `resitance_14_21Tolerant` - `resitance_14_21TolerantSD`, ymax = `resitance_14_21Tolerant` + `resitance_14_21TolerantSD`), width = 0.2,
                position = position_dodge(0.05), color = "black") + 
  labs(x = "Eukaryotic Order", y = "Log fold change", 
       title = "Log Fold Change in ANCOM Significant Taxa: Tolerant vs Super Resistant ") + 
  theme_bw() + 
  theme(legend.position = "none",
        panel.grid.minor.y = element_blank()) + coord_flip() + scale_y_continuous(limits = c(-3, 3))
T_SR

library("ggpubr")
pdf("/Volumes/GoogleDrive/.shortcut-targets-by-id/1NZWDX6hj2iMLlcMpeA9ILkNyhxyngfoM/Bonacolta\ et\ al.\ 2020\ Paramuricea/manuscript/figures/main\ figs/raw/Fig10S-ANCOM-EUK.pdf", width=10.8, height=30)
ggarrange(HS_S, HS_T, HS_R, HS_SR, S_T, S_R, S_SR, T_R, T_SR, R_RS, nrow=10, common.legend = TRUE, legend="none")
dev.off()
```


```{r}
library(ANCOMBC)
library(DT)
noport <- subset_samples(psf_euk_coral_Tmin, psf_euk_coral_Tmin@sam_data$region!="Portugal")

notol <- subset_samples(noport, noport@sam_data$resitance_14_21!="Tolerant")
# Re-code groups so that all resistance or together
sample_data(notol)$resitance_14_21 = recode(sample_data(notol)$resitance_14_21,
                                     Hypersensible = "Sensitive",
                                     Sensible = "Sensitive",
                                     Resistant = "Resistant",
                                     Superresistant = "Resistant")


# Aggregate to phylum level
genus_data = aggregate_taxa(noport, "Genus")
out = ancombc(phyloseq = genus_data, formula = "resitance_14_21", 
              p_adj_method = "holm", zero_cut = 0.99, lib_cut = 0, 
              group = "resitance_14_21", struc_zero = TRUE, neg_lb = TRUE, tol = 1e-5, 
              max_iter = 100, conserve = TRUE, alpha = 0.05, global = TRUE)

res = out$res
res_global = out$res_global


tab_coef = res$beta
tab_coef %>% datatable(caption = "Coefficients from the Primary Result") %>%
      formatRound(colnames(tab_coef), digits = 2)

tab_w = res$W
tab_w %>% datatable(caption = "Test Statistics from the Primary Result") %>%
      formatRound(colnames(tab_w), digits = 2)

tab_p = res$p_val
tab_p %>% datatable(caption = "P-values from the Primary Result") %>%
      formatRound(colnames(tab_p), digits = 2)

tab_q = res$q
tab_q %>% datatable(caption = "Adjusted p-values from the Primary Result") %>%
      formatRound(colnames(tab_q), digits = 2)


tab_diff = res$diff_abn
tab_diff %>% 
  datatable(caption = "Differentially Abundant Taxa 
            from the Primary Result")

samp_frac = out$samp_frac
# Replace NA with 0
samp_frac[is.na(samp_frac)] = 0 

# Add pesudo-count (1) to avoid taking the log of 0
log_obs_abn = log(abundances(genus_data) + 1) 
# Adjust the log observed abundances
log_obs_abn_adj = t(t(log_obs_abn) - samp_frac)
# Show the first 6 samples
round(log_obs_abn_adj[, 1:6], 2) %>% 
  datatable(caption = "Bias-adjusted log observed abundances")


df_fig1 = data.frame(res$beta * res$diff_abn, check.names = FALSE) %>% 
  rownames_to_column("taxon_id")
df_fig2 = data.frame(res$se * res$diff_abn, check.names = FALSE) %>% 
  rownames_to_column("taxon_id")
colnames(df_fig2)[-1] = paste0(colnames(df_fig2)[-1], "SD")
df_fig = df_fig1 %>% left_join(df_fig2, by = "taxon_id") %>%
  transmute(taxon_id, resitance_14_21Superresistant, resitance_14_21SuperresistantSD) %>% 
  filter(resitance_14_21Superresistant != 0) %>% arrange(desc(resitance_14_21Superresistant)) %>%
  mutate(group = ifelse(resitance_14_21Superresistant > 0, "g1", "g2"))
df_fig$taxon_id = factor(df_fig$taxon_id, levels = df_fig$taxon_id)
  
p = ggplot(data = df_fig, 
           aes(x = taxon_id, y = resitance_14_21Superresistant, fill = resitance_14_21Superresistant, color = resitance_14_21Superresistant)) + 
  geom_bar(stat = "identity", width = 0.7, 
           position = position_dodge(width = 0.4)) +
  geom_errorbar(aes(ymin = resitance_14_21Superresistant - resitance_14_21SuperresistantSD, ymax = resitance_14_21Superresistant + resitance_14_21SuperresistantSD), width = 0.2,
                position = position_dodge(0.05), color = "black") + 
  labs(x = NULL, y = "Log fold change", 
       title = "Log Fold Change Superresistant vs Sensitive") + 
  theme_bw() + 
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5),
        panel.grid.minor.y = element_blank(),
        axis.text.x = element_text(angle = 60, hjust = 1))
p
```
```{r}
library(ANCOMBC)
library(DT)
noport <- subset_samples(psf_euk_coral_Tmin, psf_euk_coral_Tmin@sam_data$region!="Portugal")

#notol <- subset_samples(noport, noport@sam_data$resitance_14_21!="Tolerant")
# Re-code groups so that all resistance or together
#sample_data(notol)$resitance_14_21 = recode(sample_data(notol)$resitance_14_21,
#                                     Hypersensible = "Sensitive",
#                                     Sensible = "Sensitive",
#                                     Resistant = "Resistant",
#                                     Superresistant = "Resistant")


# Aggregate to phylum level

oldtax <- data.frame(tax_table(noport))

oldtax$Order[oldtax$Order == "Dinophyceae_X"] <- "Dinophyceae IS"
oldtax$Order[oldtax$Order == "Prymnesiophyceae_X"] <- "Prymnesiophyceae IS"
oldtax$Order[oldtax$Order == "Prasino-Clade-9_NA"] <- "Prasino-Clade-9 IS"
oldtax$Order[oldtax$Order == "Apicomplexa_X"] <- "Apicomplexa IS"
oldtax$Order[oldtax$Order == "Dinoflagellata_X"] <- "Dinoflagellata IS"
oldtax$Order[oldtax$Order == "Coccidiomorphea_NA"] <- "Coccidiomorphea IS"
oldtax$Order[oldtax$Order == "Alveolata_X"] <- "Alveolata IS"
oldtax$Order[oldtax$Order == "Dinophyceae_NA"] <- "Dinophyceae IS"
oldtax$Order[oldtax$Order == "Eukaryota_X"] <- "Eukaryota IS"
oldtax$Order[oldtax$Order == "Dinophyceae_NA"] <- "Dinophyceae IS"
oldtax$Order[oldtax$Order == "Prymnesiophyceae_NA"] <- "Prymnesiophyceae IS"
oldtax$Order[oldtax$Order == "Prasino-Clade-9_X"] <- "Prasino-Clade-9 IS"
oldtax$Order[oldtax$Order == "Apicomplexa_NA"] <- "Apicomplexa IS"
oldtax$Order[oldtax$Order == "Dinoflagellata_NA"] <- "Dinoflagellata IS"
oldtax$Order[oldtax$Order == "Coccidiomorphea_X"] <- "Coccidiomorphea IS"
oldtax$Order[oldtax$Order == "Alveolata_NA"] <- "Alveolata IS"
oldtax$Order[oldtax$Order == "Dinophyceae_X"] <- "Dinophyceae IS"
oldtax$Order[oldtax$Order == "Eukaryota_NA"] <- "Eukaryota IS"

tax_table(noport) <- as.matrix(oldtax)
genus_data = aggregate_taxa(noport, "Order")

out = ancombc(phyloseq = genus_data, formula = "resitance_14_21", 
              p_adj_method = "holm", zero_cut = 0.99, lib_cut = 0, 
              group = "resitance_14_21", struc_zero = TRUE, neg_lb = TRUE, tol = 1e-5, 
              max_iter = 100, conserve = TRUE, alpha = 0.05, global = TRUE)

res = out$res
res_global = out$res_global


tab_coef = res$beta
tab_coef %>% datatable(caption = "Coefficients from the Primary Result") %>%
      formatRound(colnames(tab_coef), digits = 2)

tab_w = res$W
tab_w %>% datatable(caption = "Test Statistics from the Primary Result") %>%
      formatRound(colnames(tab_w), digits = 2)

tab_p = res$p_val
tab_p %>% datatable(caption = "P-values from the Primary Result") %>%
      formatRound(colnames(tab_p), digits = 2)

tab_q = res$q
tab_q %>% datatable(caption = "Adjusted p-values from the Primary Result") %>%
      formatRound(colnames(tab_q), digits = 2)


tab_diff = res$diff_abn
tab_diff %>% 
  datatable(caption = "Differentially Abundant Taxa 
            from the Primary Result")

samp_frac = out$samp_frac
# Replace NA with 0
samp_frac[is.na(samp_frac)] = 0 

# Add pesudo-count (1) to avoid taking the log of 0
log_obs_abn = log(abundances(genus_data) + 1) 
# Adjust the log observed abundances
log_obs_abn_adj = t(t(log_obs_abn) - samp_frac)
# Show the first 6 samples
round(log_obs_abn_adj[, 1:6], 2) %>% 
  datatable(caption = "Bias-adjusted log observed abundances")


df_fig1 = data.frame(res$beta * res$diff_abn, check.names = FALSE) %>% 
  rownames_to_column("taxon_id")
df_fig2 = data.frame(res$se * res$diff_abn, check.names = FALSE) %>% 
  rownames_to_column("taxon_id")
colnames(df_fig2)[-1] = paste0(colnames(df_fig2)[-1], "SD")
df_fig = df_fig1 %>% left_join(df_fig2, by = "taxon_id") %>%
  transmute(taxon_id, resitance_14_21Superresistant, resitance_14_21SuperresistantSD) %>% 
  filter(resitance_14_21Superresistant != 0) %>% arrange(desc(resitance_14_21Superresistant)) %>%
  mutate(group = ifelse(resitance_14_21Superresistant > 0, "g1", "g2"))
df_fig$taxon_id = factor(df_fig$taxon_id, levels = df_fig$taxon_id)
  
p = ggplot(data = df_fig, 
           aes(x = taxon_id, y = resitance_14_21Superresistant, fill = resitance_14_21Superresistant, color = resitance_14_21Superresistant)) + 
  geom_bar(stat = "identity", width = 0.7, 
           position = position_dodge(width = 0.4)) + scale_fill_viridis_c(option = "plasma") + scale_color_viridis_c(option = "plasma") +
  geom_errorbar(aes(ymin = resitance_14_21Superresistant - resitance_14_21SuperresistantSD, ymax = resitance_14_21Superresistant + resitance_14_21SuperresistantSD), width = 0.2,
                position = position_dodge(0.05), color = "black") + 
  labs(x = "Eukaryotic Order", y = "Log fold change", 
       title = "ANCOM Log Fold Change: Superresistant vs Hypersensitive") + 
  theme_bw() + 
  theme(legend.position = "none",
        panel.grid.minor.y = element_blank()) + coord_flip()
p

pdf("/Volumes/GoogleDrive/.shortcut-targets-by-id/1NZWDX6hj2iMLlcMpeA9ILkNyhxyngfoM/Bonacolta\ et\ al.\ 2020\ Paramuricea/manuscript/figures/ANCOMBC.pdf",  width=8, height=6)
plot(p)
dev.off()
```


```{r}
res
res_global

samp_frac = out$samp_frac
# Replace NA with 0
samp_frac[is.na(samp_frac)] = 0 

# Add pesudo-count (1) to avoid taking the log of 0
log_obs_abn = log(abundances(genus_data) + 1) 
# Adjust the log observed abundances
log_obs_abn_adj = t(t(log_obs_abn) - samp_frac)
# Show the first 6 samples
round(log_obs_abn_adj[, 1:6], 2) %>% 
  datatable(caption = "Bias-adjusted log observed abundances")


df_fig1 = data.frame(res$beta * res$diff_abn, check.names = FALSE) %>% 
  rownames_to_column("taxon_id")
df_fig2 = data.frame(res$se * res$diff_abn, check.names = FALSE) %>% 
  rownames_to_column("taxon_id")
colnames(df_fig2)[-1] = paste0(colnames(df_fig2)[-1], "SD")
df_fig = df_fig1 %>% left_join(df_fig2, by = "taxon_id") %>%
  transmute(taxon_id, resitance_14_21Resistant, resitance_14_21ResistantSD) %>% 
  filter(resitance_14_21Resistant != 0) %>% arrange(desc(resitance_14_21Resistant)) %>%
  mutate(group = ifelse(resitance_14_21Resistant > 0, "g1", "g2"))
df_fig$taxon_id = factor(df_fig$taxon_id, levels = df_fig$taxon_id)
  
p = ggplot(data = df_fig, 
           aes(x = taxon_id, y = resitance_14_21Resistant, fill = resitance_14_21Resistant, color = resitance_14_21Resistant)) + 
  geom_bar(stat = "identity", width = 0.7, 
           position = position_dodge(width = 0.4)) + scale_fill_viridis_c(option = "plasma") + scale_color_viridis_c(option = "plasma") +
  geom_errorbar(aes(ymin = resitance_14_21Resistant - resitance_14_21ResistantSD, ymax = resitance_14_21Resistant + resitance_14_21ResistantSD), width = 0.2,
                position = position_dodge(0.05), color = "black") + 
  labs(x = "Eukaryotic Order", y = "Log fold change", 
       title = "ANCOM Log Fold Change: Resistant vs Hypersensitive") + 
  theme_bw() + 
  theme(legend.position = "none",
        panel.grid.minor.y = element_blank()) + coord_flip()
p

pdf("/Volumes/GoogleDrive/.shortcut-targets-by-id/1NZWDX6hj2iMLlcMpeA9ILkNyhxyngfoM/Bonacolta\ et\ al.\ 2020\ Paramuricea/manuscript/figures/supplemental/ANCOMBC-Resistant.pdf",  width=8, height=6)
plot(p)
dev.off()
```

```{r}
df_fig1 = data.frame(res$beta * res$diff_abn, check.names = FALSE) %>% 
  rownames_to_column("taxon_id")
df_fig2 = data.frame(res$se * res$diff_abn, check.names = FALSE) %>% 
  rownames_to_column("taxon_id")
colnames(df_fig2)[-1] = paste0(colnames(df_fig2)[-1], "SD")
df_fig = df_fig1 %>% left_join(df_fig2, by = "taxon_id") %>%
  transmute(taxon_id, resitance_14_21Sensible, resitance_14_21SensibleSD) %>% 
  filter(resitance_14_21Sensible != 0) %>% arrange(desc(resitance_14_21Sensible)) %>%
  mutate(group = ifelse(resitance_14_21Sensible > 0, "g1", "g2"))
df_fig$taxon_id = factor(df_fig$taxon_id, levels = df_fig$taxon_id)
  
p = ggplot(data = df_fig, 
           aes(x = taxon_id, y = resitance_14_21Sensible, fill = resitance_14_21Sensible, color = resitance_14_21Sensible)) + 
  geom_bar(stat = "identity", width = 0.7, 
           position = position_dodge(width = 0.4)) + scale_fill_viridis_c(option = "plasma") + scale_color_viridis_c(option = "plasma") +
  geom_errorbar(aes(ymin = resitance_14_21Sensible - resitance_14_21SensibleSD, ymax = resitance_14_21Sensible + resitance_14_21SensibleSD), width = 0.2,
                position = position_dodge(0.05), color = "black") + 
  labs(x = "Eukaryotic Order", y = "Log fold change", 
       title = "ANCOM Log Fold Change: Sensitive vs Hypersensitive") + 
  theme_bw() + 
  theme(legend.position = "none",
        panel.grid.minor.y = element_blank()) + coord_flip()
p

pdf("/Volumes/GoogleDrive/.shortcut-targets-by-id/1NZWDX6hj2iMLlcMpeA9ILkNyhxyngfoM/Bonacolta\ et\ al.\ 2020\ Paramuricea/manuscript/figures/supplemental/ANCOMBC-Sensitive.pdf",  width=8, height=6)
plot(p)
dev.off()
res
```


```{r}
df_fig1 = data.frame(res$beta * res$diff_abn, check.names = FALSE) %>% 
  rownames_to_column("taxon_id")
df_fig2 = data.frame(res$se * res$diff_abn, check.names = FALSE) %>% 
  rownames_to_column("taxon_id")
colnames(df_fig2)[-1] = paste0(colnames(df_fig2)[-1], "SD")
df_fig = df_fig1 %>% left_join(df_fig2, by = "taxon_id") %>%
  transmute(taxon_id, resitance_14_21Tolerant, resitance_14_21TolerantSD) %>% 
  filter(resitance_14_21Tolerant != 0) %>% arrange(desc(resitance_14_21Tolerant)) %>%
  mutate(group = ifelse(resitance_14_21Tolerant > 0, "g1", "g2"))
df_fig$taxon_id = factor(df_fig$taxon_id, levels = df_fig$taxon_id)
  
p = ggplot(data = df_fig, 
           aes(x = taxon_id, y = resitance_14_21Tolerant, fill = resitance_14_21Tolerant, color = resitance_14_21Tolerant)) + 
  geom_bar(stat = "identity", width = 0.7, 
           position = position_dodge(width = 0.4)) + scale_fill_viridis_c(option = "plasma") + scale_color_viridis_c(option = "plasma") +
  geom_errorbar(aes(ymin = resitance_14_21Tolerant - resitance_14_21TolerantSD, ymax = resitance_14_21Tolerant + resitance_14_21TolerantSD), width = 0.2,
                position = position_dodge(0.05), color = "black") + 
  labs(x = "Eukaryotic Order", y = "Log fold change", 
       title = "ANCOM Log Fold Change: Tolerant vs Hypersensitive") + 
  theme_bw() + 
  theme(legend.position = "none",
        panel.grid.minor.y = element_blank()) + coord_flip()
p

pdf("/Volumes/GoogleDrive/.shortcut-targets-by-id/1NZWDX6hj2iMLlcMpeA9ILkNyhxyngfoM/Bonacolta\ et\ al.\ 2020\ Paramuricea/manuscript/figures/supplemental/ANCOMBC-Tolerant.pdf",  width=8, height=6)
plot(p)
dev.off()
```

### Now change categories so its just 2, remove tolerant. 

```{r}
library(ANCOMBC)
library(DT)
noport <- subset_samples(psf_euk_coral_Tmin, psf_euk_coral_Tmin@sam_data$region!="Portugal")

notol <- subset_samples(noport, noport@sam_data$resitance_14_21!="Tolerant")
# Re-code groups so that all resistance or together
sample_data(notol)$resitance_14_21 = recode(sample_data(notol)$resitance_14_21,
                                  Hypersensible = "Sensitive",
                                  Sensible = "Sensitive",
                                  Resistant = "Resistant",
                                  Superresistant = "Resistant")


# Aggregate to phylum level

oldtax <- data.frame(tax_table(notol))

oldtax$Order[oldtax$Order == "Dinophyceae_X"] <- "Dinophyceae IS"
oldtax$Order[oldtax$Order == "Prymnesiophyceae_X"] <- "Prymnesiophyceae IS"
oldtax$Order[oldtax$Order == "Prasino-Clade-9_NA"] <- "Prasino-Clade-9 IS"
oldtax$Order[oldtax$Order == "Apicomplexa_X"] <- "Apicomplexa IS"
oldtax$Order[oldtax$Order == "Dinoflagellata_X"] <- "Dinoflagellata IS"
oldtax$Order[oldtax$Order == "Coccidiomorphea_NA"] <- "Coccidiomorphea IS"
oldtax$Order[oldtax$Order == "Alveolata_X"] <- "Alveolata IS"
oldtax$Order[oldtax$Order == "Dinophyceae_NA"] <- "Dinophyceae IS"
oldtax$Order[oldtax$Order == "Eukaryota_X"] <- "Eukaryota IS"
oldtax$Order[oldtax$Order == "Dinophyceae_NA"] <- "Dinophyceae IS"
oldtax$Order[oldtax$Order == "Prymnesiophyceae_NA"] <- "Prymnesiophyceae IS"
oldtax$Order[oldtax$Order == "Prasino-Clade-9_X"] <- "Prasino-Clade-9 IS"
oldtax$Order[oldtax$Order == "Apicomplexa_NA"] <- "Apicomplexa IS"
oldtax$Order[oldtax$Order == "Dinoflagellata_NA"] <- "Dinoflagellata IS"
oldtax$Order[oldtax$Order == "Coccidiomorphea_X"] <- "Coccidiomorphea IS"
oldtax$Order[oldtax$Order == "Alveolata_NA"] <- "Alveolata IS"
oldtax$Order[oldtax$Order == "Dinophyceae_X"] <- "Dinophyceae IS"
oldtax$Order[oldtax$Order == "Eukaryota_NA"] <- "Eukaryota IS"

oldtax$Order[oldtax$Order == "Phyllopharyngea_NA"] <- "Phyllopharyngea IS"
oldtax$Order[oldtax$Order == "Syndiniales_X"] <- "Syndiniales IS"
oldtax$Order[oldtax$Order == "Syndiniales_NA"] <- "Syndiniales IS"





tax_table(notol) <- as.matrix(oldtax)
genus_data = aggregate_taxa(notol, "Order")

out = ancombc(phyloseq = genus_data, formula = "resitance_14_21", 
              p_adj_method = "holm", zero_cut = 0.99, lib_cut = 0, 
              group = "resitance_14_21", struc_zero = TRUE, neg_lb = TRUE, tol = 1e-5, 
              max_iter = 100, conserve = TRUE, alpha = 0.05, global = TRUE)

res = out$res
res_global = out$res_global

tab_diff = res$diff_abn
tab_diff %>% 
  datatable(caption = "Differentially Abundant Taxa 
            from the Primary Result")

samp_frac = out$samp_frac
# Replace NA with 0
samp_frac[is.na(samp_frac)] = 0 

# Add pesudo-count (1) to avoid taking the log of 0
log_obs_abn = log(abundances(genus_data) + 1) 
# Adjust the log observed abundances
log_obs_abn_adj = t(t(log_obs_abn) - samp_frac)
# Show the first 6 samples
round(log_obs_abn_adj[, 1:6], 2) %>% 
  datatable(caption = "Bias-adjusted log observed abundances")


df_fig1 = data.frame(res$beta * res$diff_abn, check.names = FALSE) %>% 
  rownames_to_column("taxon_id")
df_fig2 = data.frame(res$se * res$diff_abn, check.names = FALSE) %>% 
  rownames_to_column("taxon_id")
colnames(df_fig2)[-1] = paste0(colnames(df_fig2)[-1], "SD")
df_fig = df_fig1 %>% left_join(df_fig2, by = "taxon_id") %>%
  transmute(taxon_id, resitance_14_21Sensitive, resitance_14_21SensitiveSD) %>% 
  filter(resitance_14_21Sensitive != 0) %>% arrange(desc(resitance_14_21Sensitive)) %>%
  mutate(group = ifelse(resitance_14_21Sensitive > 0, "g1", "g2"))
df_fig$taxon_id = factor(df_fig$taxon_id, levels = df_fig$taxon_id)
  
p = ggplot(data = df_fig, 
           aes(x = taxon_id, y = resitance_14_21Sensitive, fill = resitance_14_21Sensitive, color = resitance_14_21Sensitive)) + 
  geom_bar(stat = "identity", width = 0.7, 
           position = position_dodge(width = 0.4)) + scale_fill_viridis_c(option = "plasma") + scale_color_viridis_c(option = "plasma") +
  geom_errorbar(aes(ymin = resitance_14_21Sensitive - resitance_14_21SensitiveSD, ymax = resitance_14_21Sensitive + resitance_14_21SensitiveSD), width = 0.2,
                position = position_dodge(0.05), color = "black") + 
  labs(x = "Eukaryotic Order", y = "Log fold change", 
       title = "ANCOM Log Fold Change: Sensitive vs Resistant") + 
  theme_bw() + 
  theme(legend.position = "none",
        panel.grid.minor.y = element_blank()) + coord_flip()
p

pdf("/Volumes/GoogleDrive/.shortcut-targets-by-id/1NZWDX6hj2iMLlcMpeA9ILkNyhxyngfoM/Bonacolta\ et\ al.\ 2020\ Paramuricea/manuscript/figures/supplemental/ANCOMBC-adjusted.pdf",  width=8, height=6)
plot(p)
dev.off()
```

```{r}
library(ANCOMBC)
library(DT)
noport <- subset_samples(psf_euk_coral_Tmin, psf_euk_coral_Tmin@sam_data$region!="Portugal")

notol <- subset_samples(noport, noport@sam_data$resitance_14_21!="Tolerant")
# Re-code groups so that all resistance or together
sample_data(notol)$resitance_14_21 = recode(sample_data(notol)$resitance_14_21,
                                  Hypersensible = "Sensitive",
                                  Sensible = "Sensitive",
                                  Resistant = "Resistant",
                                  Superresistant = "Resistant")


# Aggregate to phylum level

oldtax <- data.frame(tax_table(notol))

oldtax$Order[oldtax$Order == "Dinophyceae_X"] <- "Dinophyceae IS"
oldtax$Order[oldtax$Order == "Prymnesiophyceae_X"] <- "Prymnesiophyceae IS"
oldtax$Order[oldtax$Order == "Prasino-Clade-9_NA"] <- "Prasino-Clade-9 IS"
oldtax$Order[oldtax$Order == "Apicomplexa_X"] <- "Apicomplexa IS"
oldtax$Order[oldtax$Order == "Dinoflagellata_X"] <- "Dinoflagellata IS"
oldtax$Order[oldtax$Order == "Coccidiomorphea_NA"] <- "Coccidiomorphea IS"
oldtax$Order[oldtax$Order == "Alveolata_X"] <- "Alveolata IS"
oldtax$Order[oldtax$Order == "Dinophyceae_NA"] <- "Dinophyceae IS"
oldtax$Order[oldtax$Order == "Eukaryota_X"] <- "Eukaryota IS"
oldtax$Order[oldtax$Order == "Dinophyceae_NA"] <- "Dinophyceae IS"
oldtax$Order[oldtax$Order == "Prymnesiophyceae_NA"] <- "Prymnesiophyceae IS"
oldtax$Order[oldtax$Order == "Prasino-Clade-9_X"] <- "Prasino-Clade-9 IS"
oldtax$Order[oldtax$Order == "Apicomplexa_NA"] <- "Apicomplexa IS"
oldtax$Order[oldtax$Order == "Dinoflagellata_NA"] <- "Dinoflagellata IS"
oldtax$Order[oldtax$Order == "Coccidiomorphea_X"] <- "Coccidiomorphea IS"
oldtax$Order[oldtax$Order == "Alveolata_NA"] <- "Alveolata IS"
oldtax$Order[oldtax$Order == "Dinophyceae_X"] <- "Dinophyceae IS"
oldtax$Order[oldtax$Order == "Eukaryota_NA"] <- "Eukaryota IS"

oldtax$Order[oldtax$Order == "Phyllopharyngea_NA"] <- "Phyllopharyngea IS"
oldtax$Order[oldtax$Order == "Syndiniales_X"] <- "Syndiniales IS"
oldtax$Order[oldtax$Order == "Syndiniales_NA"] <- "Syndiniales IS"





tax_table(notol) <- as.matrix(oldtax)
genus_data = aggregate_taxa(notol, "Order")

out = ancombc(phyloseq = genus_data, formula = "resitance_14_21", 
              p_adj_method = "none", zero_cut = 0.99, lib_cut = 0, 
              group = "resitance_14_21", struc_zero = TRUE, neg_lb = TRUE, tol = 1e-5, 
              max_iter = 100, conserve = TRUE, alpha = 0.05, global = TRUE)

res = out$res
res_global = out$res_global

tab_diff = res$diff_abn
tab_diff %>% 
  datatable(caption = "Differentially Abundant Taxa 
            from the Primary Result")

samp_frac = out$samp_frac
# Replace NA with 0
samp_frac[is.na(samp_frac)] = 0 

# Add pesudo-count (1) to avoid taking the log of 0
log_obs_abn = log(abundances(genus_data) + 1) 
# Adjust the log observed abundances
log_obs_abn_adj = t(t(log_obs_abn) - samp_frac)
# Show the first 6 samples
round(log_obs_abn_adj[, 1:6], 2) %>% 
  datatable(caption = "Bias-adjusted log observed abundances")


df_fig1 = data.frame(res$beta * res$diff_abn, check.names = FALSE) %>% 
  rownames_to_column("taxon_id")
df_fig2 = data.frame(res$se * res$diff_abn, check.names = FALSE) %>% 
  rownames_to_column("taxon_id")
colnames(df_fig2)[-1] = paste0(colnames(df_fig2)[-1], "SD")
df_fig = df_fig1 %>% left_join(df_fig2, by = "taxon_id") %>%
  transmute(taxon_id, resitance_14_21Sensitive, resitance_14_21SensitiveSD) %>% 
  filter(resitance_14_21Sensitive != 0) %>% arrange(desc(resitance_14_21Sensitive)) %>%
  mutate(group = ifelse(resitance_14_21Sensitive > 0, "g1", "g2"))
df_fig$taxon_id = factor(df_fig$taxon_id, levels = df_fig$taxon_id)
  
p = ggplot(data = df_fig, 
           aes(x = taxon_id, y = resitance_14_21Sensitive, fill = resitance_14_21Sensitive, color = resitance_14_21Sensitive)) + 
  geom_bar(stat = "identity", width = 0.7, 
           position = position_dodge(width = 0.4)) + scale_fill_viridis_c(option = "plasma") + scale_color_viridis_c(option = "plasma") +
  geom_errorbar(aes(ymin = resitance_14_21Sensitive - resitance_14_21SensitiveSD, ymax = resitance_14_21Sensitive + resitance_14_21SensitiveSD), width = 0.2,
                position = position_dodge(0.05), color = "black") + 
  labs(x = "Eukaryotic Order", y = "Log fold change", 
       title = "ANCOM Log Fold Change: Sensitive vs Resistant") + 
  theme_bw() + 
  theme(legend.position = "none",
        panel.grid.minor.y = element_blank()) + coord_flip()
p

pdf("/Volumes/GoogleDrive/.shortcut-targets-by-id/1NZWDX6hj2iMLlcMpeA9ILkNyhxyngfoM/Bonacolta\ et\ al.\ 2020\ Paramuricea/manuscript/figures/supplemental/ANCOMBC-nonadjusted.pdf",  width=8, height=6)
plot(p)
dev.off()
```

### Now Bact
```{r}
library(ANCOMBC)
library(DT)
#notol <- subset_samples(noport, noport@sam_data$resitance_14_21!="Tolerant")
# Re-code groups so that all resistance or together
#sample_data(notol)$resitance_14_21 = recode(sample_data(notol)$resitance_14_21,
#                                     Hypersensible = "Sensitive",
#                                     Sensible = "Sensitive",
#                                     Resistant = "Resistant",
#                                     Superresistant = "Resistant")


# Aggregate to phylum level

oldtax <- data.frame(tax_table(noport_bac))

oldtax$Order[oldtax$Order == "Gammaproteobacteria_NA"] <- "Gammaproteobacteria IS"
oldtax$Order[oldtax$Order == "Alphaproteobacteria_NA"] <- "Alphaproteobacteria IS"

tax_table(noport_bac) <- as.matrix(oldtax)
genus_data = aggregate_taxa(noport_bac, "Order")

out = ancombc(phyloseq = genus_data, formula = "resitance_14_21", 
              p_adj_method = "holm", zero_cut = 0.99, lib_cut = 0, 
              group = "resitance_14_21", struc_zero = TRUE, neg_lb = TRUE, tol = 1e-5, 
              max_iter = 100, conserve = TRUE, alpha = 0.05, global = TRUE)

res = out$res
res_global = out$res_global


tab_coef = res$beta
tab_coef %>% datatable(caption = "Coefficients from the Primary Result") %>%
      formatRound(colnames(tab_coef), digits = 2)

tab_w = res$W
tab_w %>% datatable(caption = "Test Statistics from the Primary Result") %>%
      formatRound(colnames(tab_w), digits = 2)

tab_p = res$p_val
tab_p %>% datatable(caption = "P-values from the Primary Result") %>%
      formatRound(colnames(tab_p), digits = 2)

tab_q = res$q
tab_q %>% datatable(caption = "Adjusted p-values from the Primary Result") %>%
      formatRound(colnames(tab_q), digits = 2)


tab_diff = res$diff_abn
tab_diff %>% 
  datatable(caption = "Differentially Abundant Taxa 
            from the Primary Result")

samp_frac = out$samp_frac
# Replace NA with 0
samp_frac[is.na(samp_frac)] = 0 

# Add pesudo-count (1) to avoid taking the log of 0
log_obs_abn = log(abundances(genus_data) + 1) 
# Adjust the log observed abundances
log_obs_abn_adj = t(t(log_obs_abn) - samp_frac)
# Show the first 6 samples
round(log_obs_abn_adj[, 1:6], 2) %>% 
  datatable(caption = "Bias-adjusted log observed abundances")


df_fig1 = data.frame(res$beta * res$diff_abn, check.names = FALSE) %>% 
  rownames_to_column("taxon_id")
df_fig2 = data.frame(res$se * res$diff_abn, check.names = FALSE) %>% 
  rownames_to_column("taxon_id")
colnames(df_fig2)[-1] = paste0(colnames(df_fig2)[-1], "SD")
df_fig = df_fig1 %>% left_join(df_fig2, by = "taxon_id") %>%
  transmute(taxon_id, resitance_14_21Superresistant, resitance_14_21SuperresistantSD) %>% 
  filter(resitance_14_21Superresistant != 0) %>% arrange(desc(resitance_14_21Superresistant)) %>%
  mutate(group = ifelse(resitance_14_21Superresistant > 0, "g1", "g2"))
df_fig$taxon_id = factor(df_fig$taxon_id, levels = df_fig$taxon_id)
  
p = ggplot(data = df_fig, 
           aes(x = taxon_id, y = resitance_14_21Superresistant, fill = resitance_14_21Superresistant, color = resitance_14_21Superresistant)) + 
  geom_bar(stat = "identity", width = 0.7, 
           position = position_dodge(width = 0.4)) + scale_fill_viridis_c(option = "plasma") + scale_color_viridis_c(option = "plasma") +
  geom_errorbar(aes(ymin = resitance_14_21Superresistant - resitance_14_21SuperresistantSD, ymax = resitance_14_21Superresistant + resitance_14_21SuperresistantSD), width = 0.2,
                position = position_dodge(0.05), color = "black") + 
  labs(x = "Prokaryotic Order", y = "Log fold change", 
       title = "ANCOM Log Fold Change: Superresistant vs Hypersensitive") + 
  theme_bw() + 
  theme(legend.position = "none",
        panel.grid.minor.y = element_blank()) + coord_flip()
p

pdf("/Volumes/GoogleDrive/.shortcut-targets-by-id/1NZWDX6hj2iMLlcMpeA9ILkNyhxyngfoM/Bonacolta\ et\ al.\ 2020\ Paramuricea/manuscript/figures/ANCOMBC_bac.pdf",  width=8, height=4)
plot(p)
dev.off()
```

```{r}
library(ANCOMBC)
library(DT)

noport_bac <- subset_samples(psf_bac_coral_Tmin, psf_bac_coral_Tmin@sam_data$region!="Portugal")

notol <- subset_samples(noport_bac, noport_bac@sam_data$resitance_14_21!="Tolerant")

sample_data(notol)$resitance_14_21 = recode(sample_data(notol)$resitance_14_21,
                                  Hypersensible = "Sensitive",
                                  Sensible = "Sensitive",
                                  Resistant = "Resistant",
                                  Superresistant = "Resistant")


# Aggregate to phylum level

oldtax <- data.frame(tax_table(notol))

oldtax$Order[oldtax$Order == "Gammaproteobacteria_NA"] <- "Gammaproteobacteria IS"
oldtax$Order[oldtax$Order == "Alphaproteobacteria_NA"] <- "Alphaproteobacteria IS"

tax_table(notol) <- as.matrix(oldtax)
genus_data = aggregate_taxa(notol, "Order")

out = ancombc(phyloseq = genus_data, formula = "resitance_14_21", 
              p_adj_method = "holm", zero_cut = 0.99, lib_cut = 0, 
              group = "resitance_14_21", struc_zero = TRUE, neg_lb = TRUE, tol = 1e-5, 
              max_iter = 100, conserve = TRUE, alpha = 0.05, global = TRUE)

res = out$res
res_global = out$res_global

samp_frac = out$samp_frac
# Replace NA with 0
samp_frac[is.na(samp_frac)] = 0 

# Add pesudo-count (1) to avoid taking the log of 0
log_obs_abn = log(abundances(genus_data) + 1) 
# Adjust the log observed abundances
log_obs_abn_adj = t(t(log_obs_abn) - samp_frac)
# Show the first 6 samples
round(log_obs_abn_adj[, 1:6], 2) %>% 
  datatable(caption = "Bias-adjusted log observed abundances")


df_fig1 = data.frame(res$beta * res$diff_abn, check.names = FALSE) %>% 
  rownames_to_column("taxon_id")
df_fig2 = data.frame(res$se * res$diff_abn, check.names = FALSE) %>% 
  rownames_to_column("taxon_id")
colnames(df_fig2)[-1] = paste0(colnames(df_fig2)[-1], "SD")
df_fig = df_fig1 %>% left_join(df_fig2, by = "taxon_id") %>%
  transmute(taxon_id, resitance_14_21Sensitive, resitance_14_21SensitiveSD) %>% 
  filter(resitance_14_21Sensitive != 0) %>% arrange(desc(resitance_14_21Sensitive)) %>%
  mutate(group = ifelse(resitance_14_21Sensitive > 0, "g1", "g2"))
df_fig$taxon_id = factor(df_fig$taxon_id, levels = df_fig$taxon_id)
  
p = ggplot(data = df_fig, 
           aes(x = taxon_id, y = resitance_14_21Sensitive, fill = resitance_14_21Sensitive, color = resitance_14_21Sensitive)) + 
  geom_bar(stat = "identity", width = 0.7, 
           position = position_dodge(width = 0.4)) + scale_fill_viridis_c(option = "plasma") + scale_color_viridis_c(option = "plasma") +
  geom_errorbar(aes(ymin = resitance_14_21Sensitive - resitance_14_21SensitiveSD, ymax = resitance_14_21Sensitive + resitance_14_21SensitiveSD), width = 0.2,
                position = position_dodge(0.05), color = "black") + 
  labs(x = "Prokaryotic Order", y = "Log fold change", 
       title = "ANCOM Log Fold Change: Sensitive vs Resistant") + 
  theme_bw() + 
  theme(legend.position = "none",
        panel.grid.minor.y = element_blank()) + coord_flip()
p

pdf("/Volumes/GoogleDrive/.shortcut-targets-by-id/1NZWDX6hj2iMLlcMpeA9ILkNyhxyngfoM/Bonacolta\ et\ al.\ 2020\ Paramuricea/manuscript/figures/ANCOMBC_bac_adjusted.pdf",  width=8, height=4)
plot(p)
dev.off()
```



